---
output:
  bookdown::pdf_document2:
  # bookdown::word_document2:
  #   reference_docx: "word-template.docx"
    toc: no
    number_sections: no
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
    keep_tex: no
# header-includes:
  # - \usepackage{bbm}
  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \setlength{\headheight}{15pt}
  # - \lhead{Hoffmann and Velasco}
  # - \rhead{PAA 2024 Abstract}
editor_options: 
  chunk_output_type: console
  
citeproc: no
# fontfamily: mathpazo
mainfont: "Times New Roman"
fontsize: 12pt
geometry: margin=0.75in
indent: yes
link-citations: yes
linkcolor: blue
bibliography: "/Users/nathan/My Drive/Projects/2020 Same-Sex Immigrant Couples/Same-Sex Immigration.bib"
# csl: chicago-author-date.csl
# title: "How Sexuality Affects Evaluations of Immigrant Deservingness and Cultural Similarity: A Conjoint Survey Experiment"
# subtitle: "PAA 2024 Submission"
# date: "`r format(Sys.time(), '%B %e, %Y')`"
# author:
  
# Abstract: "Do Americans view lesbian and gay (LG) migrants as more deserving to enter the country than their straight counterparts? Recent changes in federal policy have contributed to significant increases in LG migrants coming to the U.S., yet little is known about how Americans view them. While Americans are increasingly polarized on their views toward migration, support for gay and lesbian migrants may be cross-cutting. Using a conjoint survey experiment of 1,650 respondents, this project investigates how immigrants' sexual minority status affects Americans' perceptions of their deservingness for admission and how this may be related to evaluations of cultural similarity. Analyses consider interactions between reason for migration, skill, and sexuality as well as heterogeneous effects based on respondent profiles. Preliminary results show that Americans are more likely to choose LG migrants for admission than straight ones; LG immigrants fleeing persecution are seen as especially deserving of admission; and Republicans, Christians, and straight respondents see LG migrants as less deserving. This paper helps disentangle Americans' preferences for migrants' presumed cultural similarity from economic potential and humanitarian merit as well as elucidate public opinion of this under-studied group of sexual minority migrants."
---

\newcommand{\tabitem}{~~\llap{\textbullet}~~}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, 
                      dpi = 300)
library(here)
library(huxtable)
library(haven)
library(patchwork)
library(cregg)
library(rdss)
library(DeclareDesign)
library(tidyverse)

options("yaml.eval.expr" = TRUE)

theme_set(theme_classic(base_family = 'Palatino') + 
            theme(legend.title=element_blank(),
                  panel.grid.major.y = element_line('grey80'),
                  legend.background = element_rect(fill = "transparent")))
ggplot <- function(...) ggplot2::ggplot(...) + scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2")
```

```{r load}
prolific <- read_csv(here('data', 'prolific.csv')) %>%
  filter(Status == 'APPROVED' | Status == 'AWAITING REVIEW')
col_names <- names(read_csv(here('data', 'survey.csv'), n_max = 0))
survey_raw <- read_csv(here('data', 'survey.csv'), col_names = col_names, skip = 3) %>%
  filter(PROLIFIC_PID %in% prolific$`Participant id`,
         PROLIFIC_PID != '644af405d31dd25adf037157', # failed attention check
         PROLIFIC_PID != '6048622d518a190008dfbe38', # extra person
         Finished == T)
# 
# not_approved <- prolific %>%
#   filter(Status != 'APPROVED') %>%
#   pull(`Participant id`)
# filter(survey_raw, PROLIFIC_PID %in% not_approved) %>%
#   select(Finished, PROLIFIC_PID)
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$prolific_pid)) %>%
#   arrange(`Participant id`) %>%
#   select(`Participant id`, Status)
# 
# unfinished_maybe <- survey_raw %>%
#   filter(Finished != T) %>%
#   pull(PROLIFIC_PID)
# finished_ids <- survey_raw %>%
#   filter(Finished == T) %>%
#   pull(PROLIFIC_PID)
# unfinished <- unfinished_maybe[!(unfinished_maybe %in% finished_ids)]
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   View()
# 
# survey_raw %>%
#   filter(Finished != T) %>%
#   View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished)
# 
# survey_raw %>%
#   filter(PROLIFIC_PID == '6111811553d54da81ce61f21') %>% View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   arrange(PROLIFIC_PID) %>%
#   select(PROLIFIC_PID, Finished)
#   group_by(PROLIFIC_PID) %>% count()
#   select(PROLIFIC_PID, everything()) %>% View()
# 
# survey_raw %>%
#   filter(!(PROLIFIC_PID %in% prolific$`Participant id`)) %>%
#   select(PROLIFIC_PID)
# 
# survey_raw %>%
#   arrange(PROLIFIC_PID) %>%
#   group_by(PROLIFIC_PID) %>%
#   filter(n()>1) %>% 
#   select(PROLIFIC_PID, everything()) %>%
#   View()
# 
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$PROLIFIC_PID)) %>%
#   select(`Participant id`)
# 
# survey_raw %>% filter(PROLIFIC_PID %in% 
#                         c('5a91877e777df200015fa0f5',
#                           '608a58c50e40c85b2f5f94ec',
#                           '6111811553d54da81ce61f21',
#                           '60fd957e79d70d6be755ad8c')) %>% View()


# Attention check
  # survey_raw %>%
  #   filter(!str_detect(tolower(attention_color_5_TEXT), 'green') |
  #            !(str_detect(as.character(attention_number_6_TEXT), '9') |
  #               str_detect(tolower(as.character(attention_number_6_TEXT)), 'nine'))
  #          ) %>%
  #   mutate(minutes = `Duration (in seconds)`/60) %>%
  #   select(prolific_pid, attention_color_5_TEXT, attention_number_6_TEXT, minutes)



survey <- survey_raw %>%
  #mutate(choice1 = Q3, choice2 = Q3, choice3 = Q13, choice4 = Q13) %>%
  pivot_longer(c(gender1:reason4, rating1:value2, rating3:value4), 
               names_to = c('.value', 'number'), names_pattern = ('(.*)(\\d+)')) %>%
  filter(!is.na(gender)) %>%
  mutate(
    chosen = case_when(
      choice_a == 'Immigrant 1 should be admitted.' & number == 1 ~ 1,
      choice_a == 'Immigrant 2 should be admitted.' & number == 2 ~ 1,
      choice_b == 'Immigrant 3 should be admitted.' & number == 3 ~ 1,
      choice_b == 'Immigrant 4 should be admitted.' & number == 4 ~ 1,
      choice_c == 'Immigrant 5 should be admitted.' & number == 5 ~ 1,
      choice_c == 'Immigrant 6 should be admitted.' & number == 6 ~ 1,
      choice_d == 'Immigrant 7 should be admitted.' & number == 7 ~ 1,
      choice_d == 'Immigrant 8 should be admitted.' & number == 8 ~ 1,
      T ~ 0),
    value_chosen = case_when(
      value_a == 'Immigrant 1 has greater shared values with the U.S.' & number == 1 ~ 1,
      value_a == 'Immigrant 2 has greater shared values with the U.S.' & number == 2 ~ 1,
      value_b == 'Immigrant 3 has greater shared values with the U.S.' & number == 3 ~ 1,
      value_b == 'Immigrant 4 has greater shared values with the U.S.' & number == 4 ~ 1,
      value_c == 'Immigrant 5 has greater shared values with the U.S.' & number == 5 ~ 1,
      value_c == 'Immigrant 6 has greater shared values with the U.S.' & number == 6 ~ 1,
      value_d == 'Immigrant 7 has greater shared values with the U.S.' & number == 7 ~ 1,
      value_d == 'Immigrant 8 has greater shared values with the U.S.' & number == 8 ~ 1,
      T ~ 0),
    sexuality = factor(ifelse(sexuality %in% c('lesbian', 'gay'), 'lesbian or gay', 'straight'), 
                       levels = c('straight', 'lesbian or gay')),
    across(c(gender, sexuality, gdp, skill, lang, religion, reason), function(x) factor(x)),
    across(c(rating, value), function(x) as.numeric(substr(x, 1,1)))) %>%
  mutate(skill = recode(skill, 
                        'has a high school degree, and works as a restaurant manager' = 
                          'high school',
                        'has a primary school education, and works as a cleaner' = 
                          'primary school',
                        'has an MD, and works as a cardiologist' = 'MD'),
         reason = recode(reason, 'could not find work due to high unemployment' = 
                           'could not find work'),
         resp_religion_full = resp_religion,
         resp_religion = factor(case_when(
           resp_religion %in% c('Other Christian', '
                                Protestant (Baptist, Methodist, Non-denominational, Lutheran, Presbyterian, Pentecostal, Episcopalian, Reformed, Church of Christ, Jehovah’s Witness, etc.)',
                                'Roman Catholic (Catholic)') ~ 'Christian',
           resp_religion %in% c('Agnostic (not sure if there is a God)',
                                'Atheist (do not believe in God)',
                                'Nothing in particular') ~ 'Atheist/not religious',
           T ~ 'Other')),
         resp_politics = factor(ifelse(
             resp_politics %in% c('Independent', 'None of these'), 'other',
             resp_politics)),
         resp_sexuality = factor(case_when(
           resp_sexuality %in% c("I don't know the answer", 'Something else') ~ 'Other',
           resp_sexuality %in% c('Bisexual', 'Lesbian or gay') ~ 'Lesbian/gay/bisexual',
           resp_sexuality == 'Straight (that is, not gay or lesbian)' ~ 'Straight'
         )),
         resp_education = factor(resp_education),
         resp_pro_econ = resp_imm_support_1,
         resp_pro_job = resp_imm_support_2,
         resp_pro_tax = resp_imm_support_3,
         resp_pro_culture = resp_imm_support_4,
         resp_pro_help = resp_imm_support_5,
         resp_con_econ = resp_imm_support_6,
         resp_con_job = resp_imm_support_7,
         resp_con_welfare = resp_imm_support_8,
         resp_con_crime = resp_imm_support_9,
         resp_con_pop = resp_imm_support_10,
         resp_con_culture = resp_imm_support_11
  )


# survey <- survey %>% slice(rep(row_number(), each = 10)) %>%
#   mutate(prolific_pid = 1:n())

```

\begin{center}
\textbf{How Sexuality Affects Evaluations of Immigrant Deservingness and Cultural Similarity: A Conjoint Survey Experiment}
\end{center}



<!-- Do Americans view lesbian and gay (LG) migrants as more deserving to enter the U.S. than their straight counterparts? This question has yet to be evaluated, but it is important to address for two reasons. First, recent changes in federal policy have contributed to significant increases in LG migrants coming to the U.S. According to American Community Survey data, numbers of different-sex couples including immigrants increased by 22 percent from 2008 to 2019 (from 7.8 million to 9.5 million), while those of corresponding same-sex couples grew from 44 thousand to 107 thousand in the same period, an increase of 140 percent. Despite this growth, how Americans view these types of migrants is unknown.   -->

<!-- Second, while Americans are increasingly polarized regarding their views toward migration, especially along party lines, support for gay and lesbian migrants may be cross-cutting. This is because bipartisan majorities support related issues like marriage equality. And as found in Europe, some right-wing citizens support LG migrants in order to make symbolic statements about national and cultural supremacy vis-a-vis the largely Global South countries these migrants are assumed to be coming from.    -->

<!-- Therefore, this project investigates whether sexual minorities are evaluated as more deserving to enter the U.S. due to perceived cultural similarity with the U.S. We administer a conjoint survey experiment that asks respondents to choose between repeated sets of two hypothetical immigrants for admission to the U.S. Respondents are then asked to choose which profile they see as more culturally similar to the U.S. This is one of the first survey experiments to examine immigrant sexuality explicitly and to directly test a cultural similarity hypothesis for immigrant deservingness.   -->

<!-- Preliminary results show that Americans are 1.2 percent more likely to choose LG migrants for admission than straight ones; LG immigrants fleeing persecution are seen as especially deserving of admission; and Republicans, Christians, and straight respondents see LG migrants as less deserving.  -->

<!-- ### Research Questions -->

<!-- 1. How do U.S. citizens evaluate sexuality when making determinations of immigrant deservingness for admission? How does sexuality compare to more well studied topics like reason for migration and skill level of the immigrant?  -->

<!-- 2. Are gay and lesbian immigrants perceived as more culturally similar to the U.S. compared to their heterosexual counterparts? And does this increase perceived deservingness?  -->

<!-- 3. Do Americans' perceptions of sexual minority immigrants vary by their own political affiliation, religious identification, or sexuality? -->


<!-- ## Background -->

Two recent policy changes have contributed to a rapid rise in lesbian and gay (LG) immigrants in the United States. In 2011, President Obama moved to make queer refugees a "population of concern", boosting the number of successful claims. Then, in 2013, the Defense of Marriage act ended, allowing U.S. citizens to sponsor the visa of a same-sex partner for the first time. Since then, numbers of same-sex couples including immigrants increased 140 percent (from 44 thousand to 107 thousand), compared to the 22 percent increase (from 7.8 million to 9.5 million) for their heterosexual counterparts.

Little is known about how Americans view this growing group. While Americans are increasingly polarized on their views toward migration, support for gay and lesbian migrants may be cross-cutting. Using a conjoint survey experiment of 1,650 respondents, this project investigates how immigrants' sexual minority status affects Americans' perceptions of their deservingness for admission and how this may be related to evaluations of cultural similarity. Analyses consider interactions between reason for migration, skill, and sexuality as well as heterogeneous effects based on respondent profiles. Preliminary results show that Americans are more likely to choose LG migrants for admission than straight ones; LG immigrants fleeing persecution are seen as especially deserving of admission; and Republicans, Christians, and straight respondents see LG migrants as less deserving. This paper helps disentangle Americans' preferences for migrants' presumed cultural similarity from economic potential and humanitarian merit as well as elucidate public opinion of this under-studied group of sexual minority migrants.

<!-- Two recent policy changes have contributed to a rapid rise in lesbian and gay (LG) immigrants in the United States. In 2011, President Obama moved to make queer refugees a "population of concern", boosting the number of successful claims. Then, in 2013, the Defense of Marriage act ended, allowing U.S. citizens to sponsor the visa of a same-sex partner for the first time. Since then, numbers of same-sex couples including immigrants increased 140 percent (from 44 thousand to 107 thousand), compared to the 22 percent increase (from 7.8 million to 9.5 million) for their heterosexual counterparts. While most scholarship on LG immigrants focuses on cases of asylum-seekers fleeing repression, recent work suggests that the typical LG immigrant may be privileged and coming from progressive contexts. These observations raise our key research questions: To what extent do Americans leverage sexual orientation as a salient factor to determine the deservingness of potential LG immigrants? Does economic potential or humanitarian merit condition these effects? -->

## Background

<!-- Two recent policy changes have contributed to a rapid rise in lesbian and gay (LG) immigrants in the United States.  While most scholarship on LG immigrants focuses on cases of asylum-seekers fleeing repression, recent work suggests that the typical LG immigrant may be privileged and coming from progressive contexts. These observations raise our key research questions: To what extent do Americans leverage sexual orientation as a salient factor to determine the deservingness of potential LG immigrants? Does economic potential or humanitarian merit condition these effects? -->

Previous experimental work assesses how native-born respondents evaluate the "deservingness" of migrants to gain legal entry to their country. This work broadly supports three theories of deservingness: *cultural similarity*, *economic potential*, and *humanitarian merit*.

<!--  Do they see refugees persecuted for their sexuality as more deserving of entry than privileged, high-earning LGB immigrants? When considering who should migrate to the United States, how do Americans evaluate sexuality as compared to earnings potential or credible danger? -->    

We hypothesize that *cultural similarity* will be the primary mechanism through which Americans determine LG immigrant deservingness. The limited, relevant research that exists finds Americans to be biased against Muslims and non-English speakers while Christians and English speakers are viewed as more deserving. This work supports "norms-based," "sociotropic" explanations. One such norm in development is that the U.S. is welcoming of lesbian and gay individuals -- at least in international imagery. Many right-wing parties across Western democracies, too, promote gay-friendly foreign images and national identities. Often, this is done to justify opposition to supposedly homophobic Black, Brown, and Muslim immigrants or to justify foreign interventions like foreign aid conditionalities (e.g., homonationalism). Thus, just like language or religion signals cultural closeness, so too will an openly gay or lesbian sexual identity.

But theories of *economic potential* have greatest empirical support. Numerous studies find that highly educated migrants working in prestigious, high-earning professions are seen as most deserving of entry. Although economic potential is not a legal consideration when awarding refugee status, respondents find hypothetical refugees with economic potential to be more deserving. And while LG Americans experience greater rates of poverty and have lower incomes compared to straight Americans, there is popular perception of this population being wealthy. This perception may transfer over toward the deservingness of LG migrants if Americans perceive this population as similarly being wealthy or, at least, as having greater economic potential.

Additionally, work on refugees has pointed to the importance of *humanitarian merit* in matters of deservingness. While some studies find greater support in Europe for immigrants with greater economic potential, they also find that respondents favor immigrants coming for "humanitarian" rather than "economic" reasons. As repression against LG communities increases in countries like Russia, this may prime Americans to be more sympathetic toward LG migrants on humanitarian grounds.  

It is therefore important to disentangle cultural theories of immigrant deservingness from economic or humanitarian explanations. Doing so has yet to be convincingly executed -- neither for LG immigrants, specifically, nor all immigrants, generally. Part of the issue is that many of these aspects of countries and individuals are correlated. And few studies have assessed cultural similarity theory beyond religion and language. We will use sexual minority status as a measure of cultural similarity that overcomes these issues. Sexual minorities are present throughout the world, avoiding issues of country-level correlates. The present era is characterized by rapidly changing policies and attitudes regarding sexual minorities, as well as substantial global heterogeneity.    


## Methods 

We use a conjoint survey experiment to isolate components of deservingness. A conjoint design allows reliable estimation of causal effects of multiple attributes on hypothetical choices. It also allows estimation of interaction effects and heterogeneous effects based on respondent attributes. We fielded the survey in the summer of 2023 to 1,650 U.S. citizen respondents using Prolific Academic, an online survey panel tool. The survey asked respondents to read two vignettes describing hypothetical immigrants and choose the one they prefer to gain entry to the United States. Each respondent completed this task four times.   

For the immigrant profiles, we varied four attributes. Two are controls: *gender* has two levels (man and woman) and *country GDP* has two levels (moderately wealthy and poor). The other attributes test our hypotheses. *Skill* has three levels (has an MD and works as a cardiologist; has a high school degree and works as a restaurant manager; and has a primary school education and works as a cleaner). *Language* has two levels (speaks English and does not speak English), *religion* has two levels (Christian and Muslim), and *sexuality* has two levels (gay/lesbian and straight). Finally, *reason for migration* has two levels (could not find work due to high unemployment; feared government persecution). In all, this creates 192 potential profiles for respondents to evaluate.    

<!-- ## Hypotheses -->
<!-- We calculate average marginal component effects (AMCEs) for the main effects and marginal means for interactions and heterogeneous effects. A positive AMCE for lesbian/gay identity implies that presentation of a lesbian/gay profile increases respondents' favorability toward admitting that immigrant, relative to a straight profile. A higher marginal mean for lesbian/gay identity implies greater likelihood of choosing lesbian/gay immigrants for admission.   -->

<!-- - H1 (main effect): Lesbian/gay identity will have a positive AMCE, relative to straight identity. -->
<!-- - H2 (mediation): Respondents who are more likely to choose lesbian/gay profiles for admission will choose them as having more shared values with the U.S., on average. Controlling for this measure of cultural similarity will attenuate the AMCE for lesbian/gay identity. -->
<!-- - H3 (interaction): For lesbian/gay profiles, persecution will have a higher marginal mean than work as a reason for migration.   -->

<!-- Heterogeneous effects for marginal means for lesbian/gay identity:   -->

<!-- - H4a (education): Respondents with a bachelor's degree will have a higher marginal mean than other education levels -->
<!-- - H4b (political ideology): Democrats will have a higher marginal mean than Republicans -->
<!-- - H4c (religion): Christians will have a lower marginal mean than other groups -->
<!-- - H4d (sexuality): Lesbian/gay/bisexual respondents will have a higher marginal mean than straight respondents -->
<!-- - H4e (opinion): Respondents who worry about immigration contributing to overpopulation will have higher marginal means -->
<!-- - H4f (lesbian/gay contacts) Respondents who have lesbian/gay friends and family will have higher marginal means -->



## Preliminary Results
Initial analyses show that Americans are 1.2 percent more likely to choose LG migrants for admission than straight ones, but this result is not statistically significant. Across education categories, respondents see straight immigrants as more deserving than LG ones. But respondents with at least a bachelor's degree see LG immigrants as more deserving than respondents with a high school or less education. However, respondents with some college see LG immigrants as the most deserving overall, complicating our theory. Democrats see LG immigrants as more deserving than straight ones, while republicans see LG ones as far less deserving. But among Democrats, LGs have a higher marginal mean. Results for religion show that Christians see LG immigrants as less deserving than atheists and the non-religious, but no less than other religious groups. If we consider sexuality, sexual minorities see LG immigrants as more deserving that straight ones.  

Preliminary analyses of the cultural similarity question show that profiles who are seen as more culturally similar are far more likely to be chosen. However LG profiles are seen as less culturally similar. For respondents who see LG profiles as more culturally similar than straight ones, they are more likely to choose the LG profiles.




