---
output:
  bookdown::pdf_document2:
  # bookdown::word_document2:
  #   reference_docx: "word-template.docx"
    toc: no
    number_sections: no
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
    keep_tex: no
header-includes:
  - \usepackage{bbm}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \setlength{\headheight}{15pt}
  - \lhead{Hoffmann and Velasco}
  - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
editor_options: 
  chunk_output_type: console
  
citeproc: no
fontfamily: mathpazo
# mainfont: "Times New Roman"
fontsize: 12pt
geometry: margin=1in
indent: yes
link-citations: yes
linkcolor: blue
bibliography: "/Users/nathan/My Drive/Projects/2020 Same-Sex Immigrant Couples/Same-Sex Immigration.bib"
csl: chicago-author-date.csl
title: "Appendix"
subtitle: "How Sexuality Affects Evaluations of Immigrant Deservingness and Cultural Similarity: A Conjoint Survey Experiment"
# subtitle: "PAA 2024 Submission"
date: "`r format(Sys.time(), '%B %e, %Y')`"
author:
- Nathan I. Hoffmann, Department of Sociology, University of California, Los Angeles
- Kristopher Velasco, Department of Sociology, Princeton University
  

---

\newcommand{\tabitem}{~~\llap{\textbullet}~~}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, 
                      dpi = 300)

library(here)
library(huxtable)
library(haven)
library(patchwork)
library(cregg)
library(rdss)
library(DeclareDesign)
library(survey)
library(srvyr)
library(tidyverse)

options("yaml.eval.expr" = TRUE)

theme_set(theme_classic(base_family = 'Palatino') + 
            theme(legend.title=element_blank(),
                  panel.grid.major.y = element_line('grey80'),
                  legend.background = element_rect(fill = "transparent")))
ggplot <- function(...) ggplot2::ggplot(...) + scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2")
```

```{r load}
prolific <- read_csv(here('data', 'prolific.csv')) %>%
  filter(Status == 'APPROVED' | Status == 'AWAITING REVIEW')
col_names <- names(read_csv(here('data', 'survey.csv'), n_max = 0))
survey_raw <- read_csv(here('data', 'survey.csv'), col_names = col_names, skip = 3) %>%
  filter(PROLIFIC_PID %in% prolific$`Participant id`,
         PROLIFIC_PID != '644af405d31dd25adf037157', # failed attention check
         PROLIFIC_PID != '6048622d518a190008dfbe38', # extra person
         Finished == T)
# 
# not_approved <- prolific %>%
#   filter(Status != 'APPROVED') %>%
#   pull(`Participant id`)
# filter(survey_raw, PROLIFIC_PID %in% not_approved) %>%
#   select(Finished, PROLIFIC_PID)
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$prolific_pid)) %>%
#   arrange(`Participant id`) %>%
#   select(`Participant id`, Status)
# 
# unfinished_maybe <- survey_raw %>%
#   filter(Finished != T) %>%
#   pull(PROLIFIC_PID)
# finished_ids <- survey_raw %>%
#   filter(Finished == T) %>%
#   pull(PROLIFIC_PID)
# unfinished <- unfinished_maybe[!(unfinished_maybe %in% finished_ids)]
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   View()
# 
# survey_raw %>%
#   filter(Finished != T) %>%
#   View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished)
# 
# survey_raw %>%
#   filter(PROLIFIC_PID == '6111811553d54da81ce61f21') %>% View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   arrange(PROLIFIC_PID) %>%
#   select(PROLIFIC_PID, Finished)
#   group_by(PROLIFIC_PID) %>% count()
#   select(PROLIFIC_PID, everything()) %>% View()
# 
# survey_raw %>%
#   filter(!(PROLIFIC_PID %in% prolific$`Participant id`)) %>%
#   select(PROLIFIC_PID)
# 
# survey_raw %>%
#   arrange(PROLIFIC_PID) %>%
#   group_by(PROLIFIC_PID) %>%
#   filter(n()>1) %>% 
#   select(PROLIFIC_PID, everything()) %>%
#   View()
# 
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$PROLIFIC_PID)) %>%
#   select(`Participant id`)
# 
# survey_raw %>% filter(PROLIFIC_PID %in% 
#                         c('5a91877e777df200015fa0f5',
#                           '608a58c50e40c85b2f5f94ec',
#                           '6111811553d54da81ce61f21',
#                           '60fd957e79d70d6be755ad8c')) %>% View()


# Attention check
  # survey_raw %>%
  #   filter(!str_detect(tolower(attention_color_5_TEXT), 'green') |
  #            !(str_detect(as.character(attention_number_6_TEXT), '9') |
  #               str_detect(tolower(as.character(attention_number_6_TEXT)), 'nine'))
  #          ) %>%
  #   mutate(minutes = `Duration (in seconds)`/60) %>%
  #   select(prolific_pid, attention_color_5_TEXT, attention_number_6_TEXT, minutes)



survey <- survey_raw %>%
  #mutate(choice1 = Q3, choice2 = Q3, choice3 = Q13, choice4 = Q13) %>%
  pivot_longer(c(gender1:reason4, rating1:value2, rating3:value4, 
                 rating5:value6, rating7:value8), 
               names_to = c('.value', 'number'), names_pattern = ('(.*)(\\d+)')) %>%
  filter(!is.na(gender)) %>%
  mutate(
    chosen = case_when(
      choice_a == 'Immigrant 1 should be admitted.' & number == 1 ~ 1,
      choice_a == 'Immigrant 2 should be admitted.' & number == 2 ~ 1,
      choice_b == 'Immigrant 3 should be admitted.' & number == 3 ~ 1,
      choice_b == 'Immigrant 4 should be admitted.' & number == 4 ~ 1,
      choice_c == 'Immigrant 5 should be admitted.' & number == 5 ~ 1,
      choice_c == 'Immigrant 6 should be admitted.' & number == 6 ~ 1,
      choice_d == 'Immigrant 7 should be admitted.' & number == 7 ~ 1,
      choice_d == 'Immigrant 8 should be admitted.' & number == 8 ~ 1,
      T ~ 0),
    value_chosen = case_when(
      value_a == 'Immigrant 1 has greater shared values with the U.S.' & number == 1 ~ 1,
      value_a == 'Immigrant 2 has greater shared values with the U.S.' & number == 2 ~ 1,
      value_b == 'Immigrant 3 has greater shared values with the U.S.' & number == 3 ~ 1,
      value_b == 'Immigrant 4 has greater shared values with the U.S.' & number == 4 ~ 1,
      value_c == 'Immigrant 5 has greater shared values with the U.S.' & number == 5 ~ 1,
      value_c == 'Immigrant 6 has greater shared values with the U.S.' & number == 6 ~ 1,
      value_d == 'Immigrant 7 has greater shared values with the U.S.' & number == 7 ~ 1,
      value_d == 'Immigrant 8 has greater shared values with the U.S.' & number == 8 ~ 1,
      T ~ 0),
    sexuality = factor(ifelse(sexuality %in% c('lesbian', 'gay'), 'Lesbian or gay', 'Straight'), 
                       levels = c('Straight', 'Lesbian or gay')),
    across(c(gender, sexuality, gdp, skill, lang, religion, reason), function(x) factor(x)),
    across(c(rating, value), function(x) as.numeric(substr(x, 1,1)))) %>%
  mutate(skill = recode(skill, 
                        'has a high school degree, and works as a restaurant manager' = 
                          'high school',
                        'has a primary school education, and works as a cleaner' = 
                          'primary school',
                        'has an MD, and works as a cardiologist' = 'MD'),
         reason = recode(reason, 'could not find work due to high unemployment' = 
                           'could not find work'),
         resp_religion_full = resp_religion,
         resp_religion = factor(case_when(
           resp_religion %in% c('Other Christian', '
                                Protestant (Baptist, Methodist, Non-denominational, Lutheran, Presbyterian, Pentecostal, Episcopalian, Reformed, Church of Christ, Jehovah’s Witness, etc.)',
                                'Roman Catholic (Catholic)') ~ 'Christian',
           resp_religion %in% c('Agnostic (not sure if there is a God)',
                                'Atheist (do not believe in God)',
                                'Nothing in particular') ~ 'Atheist/not religious',
           T ~ 'Other')),
         resp_politics = factor(ifelse(
             resp_politics %in% c('Independent', 'None of these'), 'other',
             resp_politics)),
         resp_sexuality = factor(case_when(
           resp_sexuality %in% c("I don't know the answer", 'Something else') ~ 'Other',
           resp_sexuality %in% c('Bisexual', 'Lesbian or gay') ~ 'Lesbian/gay/bisexual',
           resp_sexuality == 'Straight (that is, not gay or lesbian)' ~ 'Straight'
         )),
         resp_education = factor(resp_education),
         resp_pro_econ = resp_imm_support_1,
         resp_pro_job = resp_imm_support_2,
         resp_pro_tax = resp_imm_support_3,
         resp_pro_culture = resp_imm_support_4,
         resp_pro_help = resp_imm_support_5,
         resp_con_econ = resp_imm_support_6,
         resp_con_job = resp_imm_support_7,
         resp_con_welfare = resp_imm_support_8,
         resp_con_crime = resp_imm_support_9,
         resp_con_pop = resp_imm_support_10,
         resp_con_culture = resp_imm_support_11
  ) %>%
  mutate(BA = factor(case_when(
    resp_education %in% c("Bachelor's degree", "Master's, doctorate, or other postgraduate degree") ~ 'BA',
    !is.na(resp_education) ~ 'no BA')),
    resp_overpop = factor(case_when(
      resp_con_pop %in% c('Agree', 'Somewhat agree') ~ 'Agree',
      resp_con_pop %in% c('Disagree', 'Somewhat disagree') ~ 'Disgree')),
    know_LG = factor(case_when(resp_knowlg %in% c('No, none', "I'm not sure") ~ 'No', 
                        T ~ 'Yes'))
    ) %>%
  left_join(mutate(prolific, resp_age = as.numeric(Age), 
                   resp_ethnicity = `Ethnicity simplified`, 
                   PROLIFIC_PID = `Participant id`) %>%
              select(-Status),
            by = 'PROLIFIC_PID') %>%
  mutate(party = resp_politics,
         age_cat = case_when(
           resp_age <= 29 ~ '18-29',
           resp_age %in% 30:49 ~ '30-49',
           resp_age %in% 50:64 ~ '50-64',
           resp_age >= 65 ~ '65+',
           is.na(resp_age) ~ 'Refused'),
         educ = case_when(
           resp_education %in% c("Bachelor's degree", 
                                 "Master's, doctorate, or other postgraduate degree") ~ "College graduate+",
           resp_education %in% c('High school', 'Less than high school') ~ "H.S. graduate or less",
           resp_education == 'Some college' ~ 'Some College'),
         gender_pew = case_when(
           resp_gender == 'Man' ~ 'A man',
           resp_gender == 'Woman' ~ 'A woman',
           resp_gender == 'Other' ~ 'In some other way')
         ) %>%
  mutate(across(c(gdp, lang, reason, gender, skill, religion), ~as.factor(str_to_sentence(.x)))) %>%
  mutate(skill = as.factor(ifelse(skill == 'Md', 'MD', as.character(skill)))) %>% 
                        #levels = c('Primary school', 'High school', 'MD'))) %>%
  mutate(Sexuality = sexuality, 
         Gender = gender,
         GDP = gdp,
         Skill = skill,
         Language = lang,
         Religion = religion,
         Reason = reason)


# survey <- survey %>% slice(rep(row_number(), each = 10)) %>%
#   mutate(prolific_pid = 1:n())


pew <- read_sav(here('data/W112_Jul22','ATP W112.sav')) %>%
  mutate(weight = WEIGHT_W112,
         party = as_factor(F_PARTY_FINAL),
         age_cat = as_factor(F_AGECAT),
         educ = as_factor(F_EDUCCAT),
         gender_pew = as_factor(F_GENDER)) %>%
  mutate(party = case_when(party %in% c('Independent', 'Something else') ~ 'other',
                                   party == 'Refused' ~ NA,
                                   T ~ party))

pew_survey <- as_survey_design(pew, weights = weight)
         
props <- pew_survey %>%
  group_by(party, age_cat, educ, gender_pew) %>%
  summarize(prop_pew = survey_prop()) %>%
  ungroup() %>%
  complete(party, age_cat, educ, gender_pew) %>%
  mutate(prop_pew = ifelse(is.na(prop_pew), 0, prop_pew)) %>%
  select(-prop_pew_se)

# party = as.character(as_factor(F_PARTY_FINAL)),
#          age_cat = as.character(as_factor(F_AGECAT)),
#          educ = as.character(as_factor(F_EDUCCAT)),
#          gender = as.character(as_factor(F_GENDER))) %>%

weights <- survey %>%
  count(party, age_cat, educ, gender_pew) %>%
  mutate(prop = n / nrow(survey)) %>%
  left_join(props) %>%
  mutate(weight = prop_pew / prop) %>%
  select(-c(n, prop, prop_pew))

survey <- survey %>%
  left_join(weights) 
  
```


# Survey Instrument

A PDF of our full Qualtrics survey is available in the supplementary material. Below is material from the core of the survey, a vignette with accompanying questions.


*Please carefully read the following two descriptions of potential immigrants to the United States. Then indicate which one you personally would prefer to see admitted to the United States.*  


> Immigrant [1/2] wishes to be admitted as an immigrant to the U.S. [He/she] comes from a [GDP] country, [Skill]. [He/she] [Language], is [Religion], and identifies as [Sexuality]. [He/she] had to leave [his/her] country because [he/she] [reason].  


Randomize:  
\begin{tabular}{p{0.3\linewidth}  p{0.5\linewidth}}
\hline
\bf{Attribute} & \bf{Vignette text} \\
\hline
Gender & \tabitem man \\
& \tabitem woman \\
 \\
Country GDP
& \tabitem moderately wealthy \\
& \tabitem low-income \\

 \\
Skill
& \tabitem has an MD and works as a cardiologist \\
& \tabitem has a high school degree and works as a restaurant manager \\
& \tabitem has a primary school education and works as a cleaner \\

 \\
Language
& \tabitem speaks English \\
& \tabitem does not speak English \\
 \\
Religion
& \tabitem Christian \\
& \tabitem Muslim \\

 \\
Sexuality
& \tabitem gay/lesbian \\
& \tabitem straight (that is, not gay/lesbian) \\
 \\
Reason for migration
& \tabitem feared government persecution \\
& \tabitem could not find work due to high unemployment \\
\hline
\end{tabular}

\newpage 

Example:  
\begin{tabular}{p{0.45\linewidth}  p{0.45\linewidth}}
\hline
\bf{Immigrant 1} & \bf{Immigrant 2} \\
\hline
Immigrant 1 is a woman from a moderately wealthy country. She has a primary school education and works as a teacher. She speaks English, is Muslim, and identifies as lesbian. She had to leave her country because she could not find work due to high unemployment.
& Immigrant 2 is a man from a low-income country. He has an MD and works as a cardiologist. He does not speak English, is Christian, and identifies as straight (that is, not gay). He had to leave his country because he feared government persecution. \\
 \hline
\end{tabular}  

\vspace{1cm}  

1. *Based on their descriptions, which of these two immigrants would you personally prefer to see admitted to the United States?*  

- Immigrant 1 should be admitted
- Immigrant 2 should be admitted
  
2. *Based on their descriptions, which of these two immigrants do you think has greater shared values with the United States?*  

- Immigrant 1 has greater shared values with the U.S.
- Immigrant 2 has greater shared values with the U.S.


# Weighted Results

To re-weight the Prolific survey sample to be closer to the U.S. population, we construct inverse probability weights using the July-August 2022 American Trends Panel (Wave 112, n = `r nrow(pew)`), based on four variables: political party, age (in four categories), education, and gender. Unfortunately, Prolific does not provide an ethnicity variable that is suitable for U.S. data. Tables \@ref(tab:desc-pew) and \@ref(tab:desc-survey) present the distributions of the weighting variables in the Pew survey and our own Prolific survey, respectively.

```{r desc-pew}
gtsummary::theme_gtsummary_compact()
pew %>%
  select(Party = party, `Age category` = age_cat, Education = educ, Gender = gender_pew) %>%
  gtsummary::tbl_summary() %>%
  gtsummary::as_hux_table() %>%
  huxtable::set_italic(c(2,7,13, 18), 1) %>%
  huxtable::theme_article() %>%
  #huxtable::set_width(1) %>%
  huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!') %>%
  huxtable::set_caption('Distributions of variables used for weighting in the Pew July-August 2022 American Trends Panel')
  
```


```{r desc-survey}
gtsummary::theme_gtsummary_compact()
survey %>%
  select(Party = party, `Age category` = age_cat, Education = educ, Gender = gender_pew) %>%
  gtsummary::tbl_summary() %>%
  gtsummary::as_hux_table() %>%
  huxtable::set_italic(c(2,6,12, 16), 1) %>%
  huxtable::theme_article() %>%
  #huxtable::set_width(1) %>%
  huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!') %>%
  huxtable::set_caption('Distributions of variables used for weighting in our 2023 survey experiment administered with Prolific') 
```


\newpage

```{r all-amces, fig.cap = 'Weighted AMCEs for admission for all attributes. Standard errors are clustered within respondent.'}

plot(cj(survey, chosen ~  Sexuality + Gender + GDP + Skill + Language + Religion + Reason, 
        weights = ~weight, id = ~prolific_pid))

```

```{r value-amces, fig.cap = 'Weighted AMCEs for cultural similarity for all attributes. Standard errors are clustered within respondent.'}

plot(cj(survey, value_chosen ~  Sexuality + Gender + GDP + Skill + Language + Religion + Reason, 
        weights = ~weight, id = ~prolific_pid)) 

```


```{r mediation, eval = T, fig.cap = 'Weighted AMCEs for admission for sexuality, stratified by whether the profile received a 6 or 7 out of 7 on cultural similarity ratings'}
mediation_cj <- survey %>%
  mutate(top_value = factor(case_when(value >= 6 ~ '6 or 7 on cultural similarity',
                               T ~ '1 to 5 on cultural similarity'))) %>% 
  cj(., chosen ~ sexuality, weights = ~weight, id = ~prolific_pid, estimate = 'amce', 
             by = ~top_value)

mediation_cj %>%
  plot() +
  ggplot2::facet_wrap(~BY, nrow = 1) +
  geom_vline(aes(xintercept = ifelse(statistic == 'mm', 0.5, 0)), size = .2)
```


```{r interaction, fig.height = 3, fig.cap = 'Weighted narginal means of the interaction between sexuality and the reason for migration'}
int_cj <- cj(survey, chosen ~ sexuality, weights = ~weight, id = ~prolific_pid, estimate = 'mm', 
             by = ~reason)
int_cj_dif <- cj(survey, chosen ~ sexuality, weights = ~weight, id = ~prolific_pid, estimate = 'mm_diff', 
                 by = ~reason)

rbind(int_cj, int_cj_dif) %>%
  mutate(BY = recode(BY, 'Could not find work' = 'Work',
                     'Feared government persecution' = 'Persecution',
                     'Feared government persecution - Could not find work' = 
                       'Persecution - Work')) %>%
  plot() + 
  ggplot2::facet_wrap(~BY, ncol = 3) +
  # geom_vline(xintercept = 0.5, size = .2)
  geom_vline(aes(xintercept = ifelse(statistic == 'mm', 0.5, 0)), size = .2)
```

```{r mm, fig.height = 6, fig.cap = 'Weighted marginal means for heterogeneous effects by respondent characteristics. Standard errors are clustered within respondent'}
cj(mutate(survey, educ = factor(educ, 
                  levels = c('H.S. graduate or less', 'Some College', 'College graduate+'))), 
                chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~educ) %>%
  mutate(variable = 'Education',
         values = educ) %>%
  bind_rows(
    cj(mutate(survey, resp_politics = factor(str_to_sentence(resp_politics), 
                  levels = c('Democrat', 'Republican', 'Other'))), 
                chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_politics) %>%
      mutate(variable = 'Politics',
             values = resp_politics)) %>%
  bind_rows(
    cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_religion) %>%
      mutate(variable = 'Religion',
             values = resp_religion)) %>%
  bind_rows(
    cj(mutate(survey, resp_sexuality = factor(ifelse(resp_sexuality == 'Straight', 
                                                 'Straight', 
                                                 'Lesbian/gay/bi/other'))), 
                chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_sexuality) %>%
      mutate(variable = 'Sexuality',
             values = resp_sexuality)) %>%
  bind_rows(
    cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_overpop) %>%
      mutate(variable = 'Overpopulation Concerns',
             values = resp_overpop)) %>%
  bind_rows(
    cj(mutate(survey, know_LG = factor(know_LG, levels = c('Yes', 'No'))), 
   chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~know_LG) %>%
     mutate(variable = 'Know LG',
            values = know_LG)) %>%
  mutate(variable = factor(variable, levels = unique({.$variable})),
         values = factor(values, levels = rev(unique({.$values})))) %>%
  ggplot(aes(x = values, y = estimate, color = level)) +
  geom_pointrange(position = position_dodge(-0.5), aes(ymin = lower, ymax = upper)) +
  geom_hline(yintercept = .5, size = .2) +
  facet_wrap(~variable, scales = 'free_y', nrow = 3) +
  coord_flip() +
  labs(x = '', y = '') +
  theme(legend.position = 'bottom')



```



