---
output:
  bookdown::pdf_document2:
  # bookdown::word_document2:
  #   reference_docx: "word-template.docx"
    toc: no
    number_sections: no
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
    keep_tex: no
header-includes:
  - \usepackage{setspace}
  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \setlength{\headheight}{15pt}
  # - \lhead{Hoffmann and Velasco}
  # - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
editor_options: 
  chunk_output_type: console
  
citeproc: no
# fontfamily: mathpazo
# mainfont: "Times New Roman"
fontsize: 12pt
geometry: margin=1in
indent: yes
link-citations: yes
linkcolor: blue
bibliography: "/Users/nathan/My Drive/Projects/2020 Same-Sex Immigrant Couples/Same-Sex Immigration.bib"
csl: chicago-author-date.csl
title: "How Sexuality Affects Evaluations of Immigrant Deservingness and Cultural Similarity: A Conjoint Survey Experiment"
# date: "`r format(Sys.time(), '%B %e, %Y')`"
# author:
# - Nathan I. Hoffmann, Department of Sociology, University of California, Los Angeles
# - Kristopher Velasco, Department of Sociology, Princeton University

  

  


abstract: "In the wake of significant increases in lesbian and gay (LG) immigration, do Americans view LG migrants as more deserving of entry to the U.S. than their straight counterparts? Using a conjoint survey experiment with 1,650 respondents, we investigate how potential immigrants' sexual-minority status affects Americans' perceptions of their deservingness for admission and their cultural similarity to the U.S. Results show that, overall, Americans do not perceive LG immigrants as more deserving than straight ones, and LG immigrants are perceived as less culturally similar. But survey results reveal heterogeneity: LG immigrants fleeing persecution are seen as more deserving of admission, and Democrats, atheists, and LG respondents consider LG migrants more deserving than straight ones. This paper helps disentangle Americans' preferences for migrants' presumed cultural similarity from economic potential and humanitarian merit as well as elucidate public opinion of an under-studied but politically salient group."

# thanks: "We thank Natasha Quadlin, Marta Tienda, Sam Trejo, and participants at the 2024 Population Association of America Annual Meeting in Columbus, Ohio, for their helpful feedback on the survey and previous versions of this paper."

---

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
<!-- \doublespacing -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, 
                      dpi = 300)

library(here)
library(huxtable)
library(haven)
library(patchwork)
library(cregg)
library(rdss)
library(DeclareDesign)
library(survey)
library(srvyr)
library(tidyverse)

options("yaml.eval.expr" = TRUE)

theme_set(theme_classic(base_family = 'Palatino') + 
            theme(legend.title=element_blank(),
                  panel.grid.major.y = element_line('grey80'),
                  legend.background = element_rect(fill = "transparent")))
ggplot <- function(...) ggplot2::ggplot(...) + scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2")

# find . -name "Icon?" -print0 | xargs -0 rm -rf
```

```{r load}
prolific <- read_csv(here('data', 'prolific.csv')) %>%
  filter(Status == 'APPROVED' | Status == 'AWAITING REVIEW')
col_names <- names(read_csv(here('data', 'survey.csv'), n_max = 0))
survey_raw <- read_csv(here('data', 'survey.csv'), col_names = col_names, skip = 3) %>%
  filter(PROLIFIC_PID %in% prolific$`Participant id`,
         PROLIFIC_PID != '644af405d31dd25adf037157', # failed attention check
         PROLIFIC_PID != '6048622d518a190008dfbe38', # extra person
         Finished == T)
# 
# not_approved <- prolific %>%
#   filter(Status != 'APPROVED') %>%
#   pull(`Participant id`)
# filter(survey_raw, PROLIFIC_PID %in% not_approved) %>%
#   select(Finished, PROLIFIC_PID)
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$prolific_pid)) %>%
#   arrange(`Participant id`) %>%
#   select(`Participant id`, Status)
# 
# unfinished_maybe <- survey_raw %>%
#   filter(Finished != T) %>%
#   pull(PROLIFIC_PID)
# finished_ids <- survey_raw %>%
#   filter(Finished == T) %>%
#   pull(PROLIFIC_PID)
# unfinished <- unfinished_maybe[!(unfinished_maybe %in% finished_ids)]
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   View()
# 
# survey_raw %>%
#   filter(Finished != T) %>%
#   View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished)
# 
# survey_raw %>%
#   filter(PROLIFIC_PID == '6111811553d54da81ce61f21') %>% View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   arrange(PROLIFIC_PID) %>%
#   select(PROLIFIC_PID, Finished)
#   group_by(PROLIFIC_PID) %>% count()
#   select(PROLIFIC_PID, everything()) %>% View()
# 
# survey_raw %>%
#   filter(!(PROLIFIC_PID %in% prolific$`Participant id`)) %>%
#   select(PROLIFIC_PID)
# 
# survey_raw %>%
#   arrange(PROLIFIC_PID) %>%
#   group_by(PROLIFIC_PID) %>%
#   filter(n()>1) %>% 
#   select(PROLIFIC_PID, everything()) %>%
#   View()
# 
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$PROLIFIC_PID)) %>%
#   select(`Participant id`)
# 
# survey_raw %>% filter(PROLIFIC_PID %in% 
#                         c('5a91877e777df200015fa0f5',
#                           '608a58c50e40c85b2f5f94ec',
#                           '6111811553d54da81ce61f21',
#                           '60fd957e79d70d6be755ad8c')) %>% View()


# Attention check
  # survey_raw %>%
  #   filter(!str_detect(tolower(attention_color_5_TEXT), 'green') |
  #            !(str_detect(as.character(attention_number_6_TEXT), '9') |
  #               str_detect(tolower(as.character(attention_number_6_TEXT)), 'nine'))
  #          ) %>%
  #   mutate(minutes = `Duration (in seconds)`/60) %>%
  #   select(prolific_pid, attention_color_5_TEXT, attention_number_6_TEXT, minutes)



survey <- survey_raw %>%
  #mutate(choice1 = Q3, choice2 = Q3, choice3 = Q13, choice4 = Q13) %>%
  pivot_longer(c(gender1:reason4, rating1:value2, rating3:value4, 
                 rating5:value6, rating7:value8), 
               names_to = c('.value', 'number'), names_pattern = ('(.*)(\\d+)')) %>%
  filter(!is.na(gender)) %>%
  mutate(
    chosen = case_when(
      choice_a == 'Immigrant 1 should be admitted.' & number == 1 ~ 1,
      choice_a == 'Immigrant 2 should be admitted.' & number == 2 ~ 1,
      choice_b == 'Immigrant 3 should be admitted.' & number == 3 ~ 1,
      choice_b == 'Immigrant 4 should be admitted.' & number == 4 ~ 1,
      choice_c == 'Immigrant 5 should be admitted.' & number == 5 ~ 1,
      choice_c == 'Immigrant 6 should be admitted.' & number == 6 ~ 1,
      choice_d == 'Immigrant 7 should be admitted.' & number == 7 ~ 1,
      choice_d == 'Immigrant 8 should be admitted.' & number == 8 ~ 1,
      T ~ 0),
    value_chosen = case_when(
      value_a == 'Immigrant 1 has greater shared values with the U.S.' & number == 1 ~ 1,
      value_a == 'Immigrant 2 has greater shared values with the U.S.' & number == 2 ~ 1,
      value_b == 'Immigrant 3 has greater shared values with the U.S.' & number == 3 ~ 1,
      value_b == 'Immigrant 4 has greater shared values with the U.S.' & number == 4 ~ 1,
      value_c == 'Immigrant 5 has greater shared values with the U.S.' & number == 5 ~ 1,
      value_c == 'Immigrant 6 has greater shared values with the U.S.' & number == 6 ~ 1,
      value_d == 'Immigrant 7 has greater shared values with the U.S.' & number == 7 ~ 1,
      value_d == 'Immigrant 8 has greater shared values with the U.S.' & number == 8 ~ 1,
      T ~ 0),
    sexuality = factor(ifelse(sexuality %in% c('lesbian', 'gay'), 'Lesbian or gay', 'Straight'), 
                       levels = c('Straight', 'Lesbian or gay')),
    across(c(gender, sexuality, gdp, skill, lang, religion, reason), function(x) factor(x)),
    across(c(rating, value), function(x) as.numeric(substr(x, 1,1)))) %>%
  mutate(skill = recode(skill, 
                        'has a high school degree, and works as a restaurant manager' = 
                          'high school',
                        'has a primary school education, and works as a cleaner' = 
                          'primary school',
                        'has an MD, and works as a cardiologist' = 'MD'),
         reason = recode(reason, 'could not find work due to high unemployment' = 
                           'could not find work'),
         resp_religion_full = resp_religion,
         resp_religion = factor(case_when(
           resp_religion %in% c('Other Christian', '
                                Protestant (Baptist, Methodist, Non-denominational, Lutheran, Presbyterian, Pentecostal, Episcopalian, Reformed, Church of Christ, Jehovah’s Witness, etc.)',
                                'Roman Catholic (Catholic)') ~ 'Christian',
           resp_religion %in% c('Agnostic (not sure if there is a God)',
                                'Atheist (do not believe in God)',
                                'Nothing in particular') ~ 'Atheist/not religious',
           T ~ 'Other')),
         resp_politics = factor(ifelse(
             resp_politics %in% c('Independent', 'None of these'), 'other',
             resp_politics)),
         resp_sexuality = factor(case_when(
           resp_sexuality %in% c("I don't know the answer", 'Something else') ~ 'Other',
           resp_sexuality %in% c('Bisexual', 'Lesbian or gay') ~ 'Lesbian/gay/bisexual',
           resp_sexuality == 'Straight (that is, not gay or lesbian)' ~ 'Straight'
         )),
         resp_education = factor(resp_education),
         resp_pro_econ = resp_imm_support_1,
         resp_pro_job = resp_imm_support_2,
         resp_pro_tax = resp_imm_support_3,
         resp_pro_culture = resp_imm_support_4,
         resp_pro_help = resp_imm_support_5,
         resp_con_econ = resp_imm_support_6,
         resp_con_job = resp_imm_support_7,
         resp_con_welfare = resp_imm_support_8,
         resp_con_crime = resp_imm_support_9,
         resp_con_pop = resp_imm_support_10,
         resp_con_culture = resp_imm_support_11
  ) %>%
  mutate(BA = factor(case_when(
    resp_education %in% c("Bachelor's degree", "Master's, doctorate, or other postgraduate degree") ~ 'BA',
    !is.na(resp_education) ~ 'no BA')),
    resp_overpop = factor(case_when(
      resp_con_pop %in% c('Agree', 'Somewhat agree') ~ 'Agree',
      resp_con_pop %in% c('Disagree', 'Somewhat disagree') ~ 'Disgree')),
    know_LG = factor(case_when(resp_knowlg %in% c('No, none', "I'm not sure") ~ 'No', 
                        T ~ 'Yes'))
    ) %>%
  left_join(mutate(prolific, resp_age = as.numeric(Age), 
                   resp_ethnicity = `Ethnicity simplified`, 
                   PROLIFIC_PID = `Participant id`) %>%
              select(-Status),
            by = 'PROLIFIC_PID') %>%
  mutate(party = resp_politics,
         age_cat = case_when(
           resp_age <= 29 ~ '18-29',
           resp_age %in% 30:49 ~ '30-49',
           resp_age %in% 50:64 ~ '50-64',
           resp_age >= 65 ~ '65+',
           is.na(resp_age) ~ 'Refused'),
         educ = case_when(
           resp_education %in% c("Bachelor's degree", 
                                 "Master's, doctorate, or other postgraduate degree") ~ "College graduate+",
           resp_education %in% c('High school', 'Less than high school') ~ "H.S. graduate or less",
           resp_education == 'Some college' ~ 'Some College'),
         gender_pew = case_when(
           resp_gender == 'Man' ~ 'A man',
           resp_gender == 'Woman' ~ 'A woman',
           resp_gender == 'Other' ~ 'In some other way')
         ) %>%
  mutate(across(c(gdp, lang, reason, gender, skill, religion), ~as.factor(str_to_sentence(.x)))) %>%
  mutate(skill = as.factor(ifelse(skill == 'Md', 'MD', as.character(skill)))) %>% 
                        #levels = c('Primary school', 'High school', 'MD'))) %>%
  mutate(Sexuality = sexuality, 
         Gender = gender,
         GDP = gdp,
         Skill = skill,
         Language = lang,
         Religion = religion,
         Reason = reason) %>%
  filter(age_cat != 'Refused')


# survey <- survey %>% slice(rep(row_number(), each = 10)) %>%
#   mutate(prolific_pid = 1:n())


pew <- read_sav(here('data/W112_Jul22','ATP W112.sav')) %>%
  mutate(weight = WEIGHT_W112,
         party = as_factor(F_PARTY_FINAL),
         age_cat = as_factor(F_AGECAT),
         educ = as_factor(F_EDUCCAT),
         gender_pew = as_factor(F_GENDER)) %>%
  mutate(party = case_when(party %in% c('Independent', 'Something else') ~ 'other',
                                   party == 'Refused' ~ NA,
                                   T ~ party))

pew_survey <- as_survey_design(pew, weights = weight)
         
props <- pew_survey %>%
  group_by(party, age_cat, educ, gender_pew) %>%
  summarize(prop_pew = survey_prop()) %>%
  ungroup() %>%
  complete(party, age_cat, educ, gender_pew) %>%
  mutate(prop_pew = ifelse(is.na(prop_pew), 0, prop_pew)) %>%
  select(-prop_pew_se)

# party = as.character(as_factor(F_PARTY_FINAL)),
#          age_cat = as.character(as_factor(F_AGECAT)),
#          educ = as.character(as_factor(F_EDUCCAT)),
#          gender = as.character(as_factor(F_GENDER))) %>%

weights <- survey %>%
  count(party, age_cat, educ, gender_pew) %>%
  mutate(prop = n / nrow(survey)) %>%
  left_join(props) %>%
  mutate(weight = prop_pew / prop) %>%
  select(-c(n, prop, prop_pew))

survey <- survey %>%
  left_join(weights) 
  
```



# Introduction
Do Americans view lesbian and gay (LG) migrants as more deserving to enter the U.S. than their straight counterparts? Recent changes in U.S. federal policy have contributed to significant increases in LG migrants [@vogler_2016; @hoffmann_2024_policy]. From 2008 to 2019, different-sex couples containing immigrants increased by 22 percent (from 7.8 million to 9.5 million), while those of corresponding same-sex couples grew by 140 percent (from 44 thousand to 107 thousand) [@hoffmann_2023_sexuality]. Despite this growth, how Americans view this emergent population is unknown. To date, there has been no empirical evaluation of Americans' perceptions of LG migrants. Aside from evaluating this case for its own sake, LG migrants are important to investigate because they lie at the intersection of two ongoing processes in American society. First, Americans are increasingly polarized on immigration, particularly along the sociotropic and cultural aspects of migration [@hainmueller_2014_public; @johnston_2020_corrigendum]. Second, there is increasing bipartisan support for some aspects of LG rights, such as marriage equality [@gallup_2023_samesex]. Moreover, positions on LG rights in international contexts often span partisan divides, conveying national and cultural supremacy vis-a-vis countries in the Global South [@alessi_2020_qualitative; @danisi_2021_queering; @turnbull-dugarte_2023_instrumentally; @puar_2007_terrorist; @martel_2018_global].  

Against this backdrop, this project investigates the perceived deservingness of sexual minorities to enter the U.S. We ask three research questions. First, how do U.S. citizens evaluate sexuality when making determinations of immigrant deservingness for admission, relative to other aspects? Second, are gay and lesbian immigrants perceived as more culturally similar to the U.S. compared to their heterosexual counterparts, and how does this relate to assessments of deservingness? Finally, how do Americans' perceptions of sexual minority immigrants vary -- such as by their own political affiliation, religious identification, or sexuality?  

To answer these, we administer a conjoint survey experiment that asks respondents to choose between two hypothetical immigrants for admission to the U.S., and they are also asked to indicate which profile they see as more culturally similar to the U.S. This is one of the first survey experiments to both examine immigrant sexuality explicitly and to directly test a cultural similarity hypothesis for immigrant deservingness.  

Results demonstrate a positive yet nonsignificant effect of sexual-minority status on perceived deservingness. When disaggregated by respondent characteristics that may be more sympathetic to both LG rights and migration -- such as Democrats and non-religious  -- positive effects reach our preferred significance threshold. Yet, despite prior literature suggesting that sexual-minority status may signal cultural similarity, these migrants are viewed as significantly *less* culturally similar compared to their heterosexual counterparts, even among groups that think they are more deserving of entry. This study contributes to literature on immigrant deservingness, political culture, and the emerging field of queer migration.

<!-- Future work is needed, then, to evaluate the mechanism driving these effects.   -->

<!-- Overall, this study contributes to the emerging literature on queer migration -- a literature driven, in part, by the rapid increase in LG immigrants in the U.S. [@luibheid_2008; @ritholtz_2023_sanctuary]. Despite increasing numbers, previous work has shed little light on how the American public views this population. Furthermore, previous studies of immigrant deservingness have rarely considered or clearly evaluated how cultural similarity might shape respondents' choices. Evaluating these questions suggests new research avenues related to both sexual minorities and migration processes. -->




# Background
Policy related to LG migrants has seen major changes in recent years. In 2011, President Barack Obama moved to make queer refugees a "population of concern" [@vogler_2016], boosting the number of successful asylum claims [@shaw_2021_lgbt]. In 2013, the end of the Defense of Marriage Act allowed U.S. citizens and permanent residents to sponsor the visa of a same-sex partner for the first time [@edwards_2013]. Likely due to these changes, numbers of same-sex couples containing immigrants increased 140 percent between 2008 and 2019 [@hoffmann_2024_policy]. While most scholarship on LG immigrants focuses on asylum-seekers and others fleeing repression [@murray_2014_real; @sam_2015_teacher; @akin_2017_queer; @dhoest_2019_learning; @giametta_2020_new; @saleh_2020_queer], recent work suggests that the typical LG immigrant may be privileged and coming from progressive contexts [@hoffmann_2023_sexuality]. These observations motivate our central question: To what extent do Americans consider sexual orientation a salient factor in evaluating the deservingness of potential migrants?

<!-- Previous experimental work assesses how native-born respondents evaluate the "deservingness" of migrants to gain legal entry to their country. This work broadly supports three theories of deservingness: *cultural similarity*, *economic potential*, and *humanitarian merit*. -->  

<!--  Do they see refugees persecuted for their sexuality as more deserving of entry than privileged, high-earning LGB immigrants? When considering who should migrate to the United States, how do Americans evaluate sexuality as compared to earnings potential or credible danger? -->    

We hypothesize that *cultural similarity* will be the primary mechanism through which Americans determine LG immigrant deservingness. Other work finds that "norms-based" and "sociotropic" explanations often account for how U.S. citizens perceive immigrant deservingness [@hainmueller_2015_hidden]. For example, Westerners are biased against Muslims and speakers of foreign languages, while Christians and speakers of the host country language are viewed more favorably [@bansak_2016_how; @donnaloja_2022_british; @avina_2024_metareanalysis]. These trends raise an important question: To what extent is a new norm developing that characterizes the U.S. as welcoming of LG individuals -- at least internationally [@novitskaya_2023_have; @snow_2020_routledge]? Many right-wing parties across Western democracies, including the United States, promote gay-friendly positions abroad [@magni_2023_why; @moreau_2018_trump; @nbc_2019_trump; @janoff_2022_queer]. Often, this is done to justify opposition to supposedly homophobic Black, Brown, and Muslim immigrants or to motivate interventions through foreign aid conditionalities (i.e., homonationalism) [@puar_2007_terrorist; @kwon_2022_multidimensional]. This promotion is enabled by the fact that U.S. public opinion is increasingly supportive of LG rights. In 2022, for example, U.S. support for marriage equality reached 71%, and 93% of Americans agreed that gays and lesbians should have equal employment rights [@gallup_2023_samesex]. These attitudes are related to both increasing U.S. LGBTQ+ identification (7.6% in 2023) and increasing contact with such individuals [@gallup_2024_lgbtq]. 

Yet there are reasons to be suspect of such national narratives. Recent adoptions of anti-LGBTQ+ policy and hardened anti-immigrant sentiments in the U.S. may mean that LG immigrants are particularly vulnerable to perceptions of cultural distance and undeservingness [@jones_2024_trans]. Americans' preferences for admission may be based on an "ideal American" rooted in family values -- such as heterosexual reproduction and commitment to Christian values -- that may stand in contrast to LG migrants [@lehr_1999_queer; @behrman_2024_statelevel]. [See also @turnbull-dugarte_2024_fine on LG surrogacy support.] Another possibility is that Americans are simply indifferent to sexuality when considering potential immigrants.  

Besides cultural similarity, previous work raises two other possible theories for how Americans might evaluate deservingness for admission. Theories of *economic potential* have the greatest empirical support. Highly educated migrants working in prestigious, high-earning professions are seen as particularly deserving of entry [@hainmueller_2010_attitudes; @helbling_2014_why; @hainmueller_2015_hidden; @donnaloja_2022_british]. Although economic potential is not a legal consideration when awarding refugee status, respondents find hypothetical refugees with economic potential to be more deserving [@bansak_2016_how; @lawlor_2021_deservingness]. And, while LG Americans experience greater rates of poverty and have lower incomes compared to straight Americans, this population is often perceived as being wealthy [@defilippis_2016_what], which could translate to perceptions of greater economic potential for LG immigrants.

Additionally, work on refugees has highlighted the importance of *humanitarian merit* in matters of deservingness. While @bansak_2016_how find greater support in Europe for immigrants with greater economic potential, they also find that respondents favor immigrants coming for "humanitarian" rather than "economic" reasons. In the Danish context, @hedegaard_2022_attitudes find that refugees are considered more deserving than economic migrants. As repression against LG communities increases in countries like Russia [@velasco_2023_transnational], this may prime Americans to be more sympathetic toward LG migrants on humanitarian grounds.

<!--- In Japan, @fraser_2022_role find that immigrants fleeing natural disaster are seen as more deserving than those migrating due to political protest, labor shortage, or civil war.  --->

It is therefore important to disentangle cultural theories of immigrant deservingness from economic or humanitarian explanations. Doing so has yet to be convincingly executed, neither for LG immigrants nor more broadly. Many of these aspects of countries and individuals are correlated, and few studies have assessed cultural similarity theory beyond religion and language. We use sexual-minority status as a measure of cultural similarity that overcomes these issues. Sexual minorities are present throughout the world, avoiding issues of country-level correlates. 

<!--- 
We propose using a conjoint survey experiment to isolate these components of deservingness [@hainmueller_2014_causal]. A conjoint design allows reliable estimation of causal effects of multiple attributes on hypothetical choices [@bansak_2021_conjoint]. It also allows estimation of interaction effects [@egami_2019_causal] and heterogeneous effects based on respondent attributes [@leeper_2020_measuring].   

To assess the degree to which sexuality matters as a sign of cultural similarity, we will randomize two other attributes of cultural similarity: language and religion. To examine the cultural similarity theory explicitly, we will also ask respondents to choose which profile they see as more culturally similar to the U.S. Furthermore, while we theorize that the deservingness of this type of immigrant may cut across typical divisions, we anticipate some heterogeneous effects across respondents. Namely, we hypothesize that respondents with greater cultural affinity with and support for LG communities will view LG migrants as more deserving. We will measure the following signals of respondents' cultural closeness: educational attainment, sexual/gender minority status, political party affiliation, and religiosity.  
--->


# Methods 

We use a conjoint survey experiment to isolate these components of deservingness [@hainmueller_2014_causal]. A conjoint design allows reliable estimation of causal effects of multiple features on hypothetical choices [@bansak_2021_conjoint]. It also allows estimation of interaction effects [@egami_2019_causal] and heterogeneous effects based on respondent attributes [@leeper_2020_measuring]. To examine the cultural similarity theory explicitly, we also ask respondents to choose which profile they see as more culturally similar to the U.S. Furthermore, while we theorize that the deservingness of this type of immigrant may cut across typical divisions, we anticipate some heterogeneous effects across respondents. Namely, we hypothesize that respondents with greater cultural affinity with and support for LG communities will view LG migrants as more deserving. We measure the following signals of respondents' cultural closeness: educational attainment, sexual/gender minority status, political party affiliation, and religiosity.    

<!-- Despite the recent rise of LG immigrants in the U.S., sexuality has been under-explored in studies of immigrant deservingness.^[@lawlor_2021_deservingness include persecution due to sexual orientation (along with religion) as a “humanitarian deservingness cues” for hypothetical asylum seeker profiles, but not for refugee profiles, and they do not disaggregate these two cues. @hedegaard_2022_attitudes list "sexuality" as a possible form of persecution for hypothetical refugee profiles, along with race, religion, nationality, or political orientation.]. We use sexual minority status as a measure of cultural similarity that overcomes these issues. Sexual minorities are present throughout the world, avoiding issues of country-level correlates. The present era is characterized by rapidly changing policies and attitudes regarding sexual minorities, as well as substantial global heterogeneity. A large majority of Americans now support same-sex marriage and other rights for same-sex couples [@ofosu_2019_samesex]. This study is one of the first survey experiments to explicitly consider immigrant sexuality.   -->

<!-- To assess the degree to which sexuality matters as a sign of cultural similarity, we randomize two other attributes of cultural similarity: language and religion.  -->



After conducting a pilot study (details in the Online Appendix §H), we fielded the main survey on June 20, 2023, to 1,650 U.S. citizen respondents using Prolific.^[This study was pre-registered on OSF, and we did not deviate from our planned analyses except where specified: https://osf.io/26wfm/?view_only=922595b5c55f40b98b77fb922c7f115d] The Online Appendix §B contains details of the ethical principles we adhered to during data collection. The conjoint survey design asks respondents to read two vignettes describing hypothetical immigrants and choose the one they prefer to gain entry to the United States. Each respondent completed this task four times. We vary seven features of immigrant profiles: gender, country GDP, skill, language, religion, sexuality, and reason for migration (see Table \@ref(tab:features) for details). In all, this creates 192 potential profiles for respondents to evaluate. We re-weight the data to better match the U.S. population as a whole, using the July-August 2022 American Trends Panel [@pew_2022_american]; see the Online Appendix §C for details. Due to missing data for age, we drop 29 respondents from analysis, resulting in final sample of 1,621.  



\begin{table}
\centering
\caption{Immigrants profiles are created by randomly drawing one value from each of these seven features}
\begin{tabular}{p{0.3\linewidth}  p{0.5\linewidth}}
\toprule 
\bf{Feature} & \bf{Vignette text} \\
\midrule
Gender & \tabitem man \\
& \tabitem woman \\
 \\
Country GDP
& \tabitem moderately wealthy \\
& \tabitem low-income \\
 \\
Skill
& \tabitem has an MD and works as a cardiologist \\
& \tabitem has a high school degree and works as a restaurant manager \\
& \tabitem has a primary school education and works as a cleaner \\
 \\
Language
& \tabitem speaks English \\
& \tabitem does not speak English \\
 \\
Religion
& \tabitem Christian \\
& \tabitem Muslim \\
 \\
Sexuality
& \tabitem gay/lesbian \\
& \tabitem straight (that is, not gay/lesbian) \\
 \\
Reason for migration
& \tabitem feared government persecution \\
& \tabitem could not find work due to high unemployment \\
\bottomrule
\end{tabular}
\label{tab:features}
\end{table}

```{r hypotheses}
read_csv(here('draft', 'hypotheses.csv')) %>%
  hux() %>%
  huxtable::theme_article() %>%
  set_valign('middle') %>%
  huxtable::set_width(1) %>%
  # huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!') %>%
  huxtable::set_caption('Pre-registered hypotheses') %>%
  huxtable::set_italic(6, 1) 
```

<!-- Two are controls: *gender* has two levels (man and woman) and *country GDP* has two levels (moderately wealthy and poor). The other attributes test our hypotheses. *Skill* has three levels (has an MD and works as a cardiologist; has a high school degree and works as a restaurant manager; and has a primary school education and works as a cleaner). *Language* has two levels (speaks English and does not speak English), *religion* has two levels (Christian and Muslim), and *sexuality* has two levels (gay/lesbian and straight). Finally, *reason for migration* has two levels (could not find work due to high unemployment; feared government persecution).  -->

One example profile reads: "Immigrant 1 wishes to be admitted as an immigrant to the United States. She comes from a moderately wealthy country, has a primary school education, and works as a cleaner. She does not speak English, is Christian, and identifies as lesbian. She had to leave her country because she could not find work due to high unemployment."  

Respondents are asked two questions: (1) "Based on their descriptions, which of these two immigrants **would you personally prefer to see admitted** to the United States?", and (2) "Based on their descriptions, which of these two immigrants do you think **has greater shared values with the United States**?" After answering these questions for four sets of profiles, respondents are asked about a variety of personal attributes. The full survey instrument is available in the Supplemental Material, with a brief overview in §A of the Online Appendix.  

In addition to estimating average marginal component effects (AMCEs) for the features of interest [@hainmueller_2014_causal], we estimate two other quantities. We examine the interaction [@egami_2019_causal] between profile sexuality and reason for migration; we expect that sexual minorities fleeing persecution will be seen as more deserving than those looking for work, and this difference may be greater for sexual minorities than straight immigrants. We also test for the presence of heterogeneous effects for subsamples of respondents [@leeper_2020_measuring], including by political party affiliation, education, religion, sexual orientation, whether someone has LG friends or family, and whether someone is concerned about overpopulation. We expect that support for LG migrants will be highest among Democrats, the highly educated, sexual minorities, those concerned about overpopulation^[Anti-immigration activists often cite overpopulation as a major reason to limit immigration [@reimers_1999_unwelcome].], and people who have close LG contacts [@lewis_2011_friends; @dellaposta_2018_gay].  

<!-- Finally, we test two mechanisms. First, we use the question on shared values to test whether the effect for LG migrants is explained by perceived cultural similarity. Second, we test the contact hypothesis [@lewis_2011_friends; @dellaposta_2018_gay] by assessing whether having gay or lesbian friends or family predicts support for gay and lesbian immigrants.   -->

We calculate average marginal component effects (AMCEs) for the main effects and marginal means for interactions and heterogeneous effects. A positive AMCE for lesbian/gay identity implies that presentation of a lesbian/gay profile increases respondents' favorability toward admitting that immigrant, relative to a straight profile. A higher marginal mean for lesbian/gay identity implies greater likelihood of choosing lesbian/gay immigrants for admission. We present our pre-registered hypotheses in Table \@ref(tab:hypotheses).^[Hypothesis H1b was not pre-registered, but it was added following a reviewer's suggestion.]




<!-- - H1 (main effect): Lesbian/gay identity will have a positive AMCE, relative to straight identity.   -->

<!-- - H2 (mediation): Respondents who are more likely to choose lesbian/gay profiles for admission will choose them as having more shared values with the U.S., on average. Controlling for this measure of cultural similarity will attenuate the AMCE for lesbian/gay identity.   -->

<!-- - H3 (interaction): For lesbian/gay profiles, persecution will have a higher marginal mean than work as a reason for migration.   -->

<!-- Heterogeneous effects for marginal means for lesbian/gay identity:   -->

<!-- - H4a (education): Respondents with a bachelor's degree will have a higher marginal mean than other education levels -->
<!-- - H4b (political ideology): Democrats will have a higher marginal mean than Republicans   -->
<!-- - H4c (religion): Christians will have a lower marginal mean than other groups   -->
<!-- - H4d (sexuality): Lesbian/gay/bisexual respondents will have a higher marginal mean than straight respondents   -->
<!-- - H4e (opinion): Respondents who worry about immigration contributing to overpopulation will have higher marginal means    -->
<!-- - H4f (lesbian/gay contacts): Respondents who have lesbian/gay friends and family will have higher marginal means -->

# Results 

```{r all-amces-calc}
all_amces <- cj(survey, chosen ~  Sexuality + Gender + GDP + Skill + Language + Religion + Reason, 
        weights = ~weight, id = ~prolific_pid)

lg_amce <- all_amces %>% filter(level == 'Lesbian or gay') %>% pull(estimate) %>% round(3)
```


Results for H1a and H1b are shown in Figure \@ref(fig:amces), which presents AMCEs for all features. (Full tables of all results are in the Online Appendix §G.) For LG profiles, we see a trivial AMCE effect size of `r lg_amce`, and it is nonsignificant. Neither H1a nor H1b is supported; overall, LG profiles are not more or less likely to be selection for admission to the U.S.

H2 hypothesized mediation, i.e. that controlling for shared values would attenuate the effect of LG profiles on being chosen for admission. Although we expected that LG profiles would be seen as more culturally similar, Figure \@ref(fig:amces) shows that this is not the case: LG profiles were *less* likely to be designated as having shared values with the U.S.^[In the Online Appendix §E, we examine how cultural similarity determinations vary by respondent characteristics. All subgroups except the non-religious see LG profiles as less culturally similar.] Although the main effect for LG profiles was nonsignificant, Figure \@ref(fig:mediation) directly assesses the mediation hypothesis, presenting AMCEs for sexuality stratified by whether the profile was designated as being more culturally similar to the U.S. Interestingly, among profiles that were designated as not having shared values with the U.S., LG profiles were significantly less likely to be chosen for admission. Among profiles chosen as quite culturally similar, LG profiles have a positive point estimate for admission (though the AMCE is nonsignificant).

<!-- Profiles who are seen as more culturally similar are far more likely to be chosen. However, LG profiles are seen as less culturally similar (Figure \@ref(fig:amces)). Even so, we assess mediation by stratifying the sample by whether profiles were in the top quartile for cultural similarity (receiving a score of 6 or 7 out of 7). For profiles that are seen as culturally similar, LG profiles are much more likely to be chosen than straight ones. For ones that are considered less culturally similar, LG profiles show no advantage. -->


```{r interaction-calc}
int_cj <- cj(survey, chosen ~ sexuality, weights = ~weight, id = ~prolific_pid, estimate = 'mm', 
             by = ~reason)
int_cj_dif <- cj(survey, chosen ~ sexuality, weights = ~weight, id = ~prolific_pid, estimate = 'mm_diff', 
                 by = ~reason)

work_int <- int_cj %>% 
  filter(BY == 'Could not find work', level == 'Lesbian or gay') %>% 
  pull(estimate) %>%
  round(3)

persecution_int <- int_cj %>% 
  filter(BY == 'Feared government persecution', level == 'Lesbian or gay') %>% 
  pull(estimate) %>%
  round(3)

LG_int_dif <- int_cj_dif %>% filter(level == 'Lesbian or gay') %>% pull(estimate) %>% round(3)
straight_int_dif <- int_cj_dif %>% filter(level == 'Straight') %>% pull(estimate) %>% round(3)
```


```{r amces, fig.cap = 'Estimated  AMCEs for admission and cultural similarity for all features. Standard errors are clustered within respondent.'}

(plot(all_amces) + 
   labs(title = 'Admission'))  + 
  (plot(cj(survey, value_chosen ~  Sexuality + Gender + GDP + Skill + Language + Religion + Reason, 
        weights = ~weight, id = ~prolific_pid))  +
     labs(title = 'Cultural Similarity') +
     theme(axis.text.y=element_blank())) +
     plot_layout(guides = 'collect') &
  theme(legend.position = 'bottom')

```



```{r mediation, eval = T, fig.height = 3, fig.cap = 'AMCEs for admission for sexuality, stratified by whether the profile received a 6 or 7 out of 7 on cultural similarity ratings'}
mediation_cj <- survey %>%
  mutate(top_value = factor(case_when(value >= 6 ~ '6 or 7 on Cultural Similarity',
                               T ~ '1 to 5 on Cultural Similarity'))) %>% 
  cj(., chosen ~ sexuality, weights = ~weight, id = ~prolific_pid, estimate = 'amce', 
             by = ~top_value)

mediation_cj %>%
  ggplot(aes(x = level, y = estimate)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  geom_hline(aes(yintercept = ifelse(statistic == 'mm', 0.5, 0)), linewidth = .2) +
  coord_flip() +
  facet_wrap(~BY, nrow = 1) +
  labs(x = '', y = '')
```


```{r interaction, fig.height = 3, fig.cap = 'Marginal means of the interaction between sexuality and the reason for migration.'}
rbind(int_cj, int_cj_dif) %>%
  mutate(BY = recode(BY, 'Could not find work' = 'Work',
                     'Feared government persecution' = 'Persecution',
                     'Feared government persecution - Could not find work' = 
                       'Persecution - Work')) %>%
  ggplot(aes(x = level, y = estimate)) +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  geom_hline(aes(yintercept = ifelse(statistic == 'mm', 0.5, 0)), linewidth = .2) +
  coord_flip() +
  facet_wrap(~BY, nrow = 1) +
  labs(x = '', y = '')
```

```{r mm, fig.height = 6, fig.cap = 'Marginal means for heterogeneous effects of choosing for admission, by respondent characteristics. Standard errors are clustered within respondent.'}
cj(mutate(survey, educ = factor(educ, 
                  levels = c('H.S. graduate or less', 'Some College', 'College graduate+'))), 
                chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~educ) %>%
  mutate(variable = 'Education',
         values = educ) %>%
  bind_rows(
    cj(mutate(survey, resp_politics = factor(str_to_sentence(resp_politics), 
                  levels = c('Democrat', 'Republican', 'Other'))), 
                chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_politics) %>%
      mutate(variable = 'Politics',
             values = resp_politics)) %>%
  bind_rows(
    cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_religion) %>%
      mutate(variable = 'Religion',
             values = resp_religion)) %>%
  bind_rows(
    cj(mutate(survey, resp_sexuality = factor(ifelse(resp_sexuality == 'Straight', 
                                                 'Straight', 
                                                 'Lesbian/gay/bi/other'))), 
                chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_sexuality) %>%
      mutate(variable = 'Sexuality',
             values = resp_sexuality)) %>%
  bind_rows(
    cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_overpop) %>%
      mutate(variable = 'Overpopulation Concerns',
             values = resp_overpop)) %>%
  bind_rows(
    cj(mutate(survey, know_LG = factor(know_LG, levels = c('Yes', 'No'))), 
   chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~know_LG) %>%
     mutate(variable = 'Know LG',
            values = know_LG)) %>%
  mutate(variable = factor(variable, levels = unique({.$variable})),
         values = factor(values, levels = rev(unique({.$values})))) %>%
  ggplot(aes(x = values, y = estimate, color = level, shape = level)) +
  geom_pointrange(position = position_dodge(-0.5), aes(ymin = lower, ymax = upper)) +
  geom_hline(yintercept = .5, linewidth = .2) +
  facet_wrap(~variable, scales = 'free_y', nrow = 3) +
  coord_flip() +
  labs(x = '', y = '') +
  theme(legend.position = 'bottom')






```


Figure \@ref(fig:interaction) presents interaction effects relevant to H3, which predicted that LG profiles with persecution as a reason for migration would be more likely to be chosen than those with economic reasons.^[In the Online Appendix §F, we present interactions with sexuality for all features.] The Figure supports this hypothesis: LG profiles that migrated to seek employment have a marginal mean of `r work_int`, while those fleeing persecution have a value of `r persecution_int`. This difference of `r LG_int_dif` is larger than the corresponding difference for straight profiles (`r straight_int_dif`), but not quite significantly so.  

Figure \@ref(fig:mm) presents marginal means relevant for H4, revealing a number of significant heterogeneous effects. H4a predicted that respondents with at least a bachelor's degree would see LG migrants as more than other educational groups. While respondents with a high school degree or less are less likely to admit LG migrants than those with a college degree, this difference is small and nonsignificant, and both groups are less likely to admit LG migrants than straight ones. Respondents with some college, on the other hand, see LG immigrants as somewhat more deserving. Regarding political ideology, Democrats see LG immigrants as  more deserving than straight ones, while Republicans see LG ones as far less deserving, in line with H4b. Results for religion support H4c: Christians see LG immigrants as less deserving than atheists and the non-religious, who are significantly more likely to admit LG migrants than straight ones. As for sexuality, sexual minorities see LG immigrants as more deserving than straight ones, in line with H4d.  

Due to the perception that LG migrants are unlikely to have children, will Americans concerned about overpopulation prefer LG migrants to straight ones (H4e)? Marginal means show the opposite effect: Respondents who worry about overpopulation are much less likely to choose LG profiles than people who do not. This is likely because overpopulation concerns are closely associated with conservative political ideologies. Finally, H4f suggested that respondents with LG family and friends would be more likely to choose LG profiles for admission, and Figure \@ref(fig:mm) supports this.  

<!-- As a robustness test, we re-weight the data to better match the U.S. population as a whole, using the July-August 2022 American Trends Panel [@pew_2022_american]. As shown in the Appendix, general trends are substantively the same as in the unweighted data, albeit with smaller effect sizes. The main effect for LG migrants is still nonsignificant, but the point estimate becomes negative. Cultural results are stable, with LG migrants perceived as less culturally similar to the U.S. For heterogeneous effects by respondent characteristics, support for LG migrants is attenuated, while support for straight migrants remains fairly stable.  -->



# Discussion and Conclusion
This conjoint survey experiment constitutes one of the first attempts to understand the rapidly growing population of lesbian and gay (LG) migrants in the wake of shifting policies and attitudes. We theorized that Americans would evaluate sexual minorities as more deserving than their straight counterparts due to perceived cultural similarity with the U.S. This prediction failed to hold: On average, U.S. citizens give no preference to LG migrants, and in fact they view them as *less* culturally similar to the U.S. than straight immigrants. Despite the U.S. promoting pro-LG positions in international affairs, this orientation does not translate to public preference for LG migrants.  

<!-- Yet, there is insufficient evidence that Americans deserve gay and lesbian migrants as more deserving of entry than their straight counterparts. Although the coefficient is in the positive direction in these models, it flips directions and maintains its nonsignificance in the weighted models included in the Appendix. One reason for this lack of effect may be because despite our theorization, Americans do not view gay and lesbian migrants as culturally similar to the U.S. In fact, profiles identifying as a sexual minority are perceived as significantly *less* culturally similar.  -->

<!-- Do Americans perceive gay and lesbian immigrants as more deserving of entry to the U.S. compared to their straight counterparts? Addressing this question is important as the number of gay and lesbian immigrants in the U.S. rose dramatically after 2010. This increase was due, in part, to changes in federal immigration policies that made LGBTQ communities a "population of concern" in the asylum process, and same-sex couples becoming eligible for fiance(é)/spousal policies after the Defense of Marriage Act was overturned [@hoffmann_2023_sexuality; @vogler_2016]. Yet, despite these increases, no study has explicitly evaluated how Americans view this population. Therefore, our conjoint survey experiment provides an important contribution to understanding how Americans perceive gay and lesbian migrants.  -->



There are three important sources of heterogeneity beneath these main effects, however. First, certain groups do see LG migrants as more deserving, including Democrats, atheists, LG people, or those who know LG people. Hence views of LG migrants may not cut across traditional attitudes toward migration or LGBTQ issues but reflect partisan polarization [@baldassarri_2008_partisans; @hout_2021_immigration]. Second, one instance in which there is overall perceived deservingness of LG migrants is when they are coming to U.S. for humanitarian reasons as opposed to economic -- supporting prior research suggests citizens support granting entry to humanitarian migrants [@bansak_2016_how; @hedegaard_2022_attitudes]. And, third, while Americans view LG migrants as less culturally similar, *when they do* find them more similar, there is some evidence that they prefer them over straight migrants.  

There are important limitations to this study that should be addressed through future research. Although we adjust our sample with population weights, future studies should use a nationally representative sample. Additionally, while our primary hypothesis is not supported, this study finds several sources of heterogeneity. If cultural similarity is not the primary driver of U.S. attitudes toward LG migrants, what is? Initial findings suggest perceived humanitarian need -- especially amid rising global backlash to LG people -- or overall partisan polarization may be more promising routes to explore. Nevertheless, this study offers an important first step toward understanding how Americans view the deservingness of LG migrants within an experimental framework. More research is needed to fully explore the contours of this dramatically growing population.


<!-- # Ethical Standards -->
<!-- The authors declare the human subjects research in this article was reviewed and approved by the [REDACTED] University Ethics Review Board (ID 15408). The authors affirm that this article adheres to the APSA’s Principles and Guidance on Human Subject Research. -->



```{r, eval = F}
# plot(cj(survey, chosen ~ sexuality, estimate = 'mm',
#         weights = ~weight, id = ~prolific_pid, by = ~ resp_politics),
#         group = 'resp_politics', size = 5, linewidth = 5) +
#   geom_vline(xintercept = .5, linewidth = .2) +
#   cowplot::theme_cowplot() +
#   theme(legend.position = 'right')

cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~ resp_politics) %>%
  mutate(BY = factor(BY, levels = c('Democrat', 'Republican', 'other'))) %>%
  rename(Politics = BY, Sexuality = level) %>%
  ggplot(aes(x = Sexuality, y = estimate, color = Politics)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), position = position_dodge(.2), size = 1) +
  coord_flip() +
  labs(y = 'Marginal means', x = '', color = NULL) +
  geom_hline(yintercept = .5, linetype = 2) +
  cowplot::theme_cowplot() +
  theme(legend.position = 'right') +
  scale_color_manual(values=c("#2774AE", "darkred", "darkgrey"))
```


```{r poster-figs, eval = F}

plot(all_amces, size = 5) +
  ggtitle('Admission') +
  cowplot::theme_cowplot(font_size = 20) +
  theme(legend.position = 'none')

ggsave(here('pres/all.png'), width = 8, height = 6)

plot(cj(survey, value_chosen ~  sexuality + gender + gdp + skill + lang + religion + reason, 
      weights = ~weight, id = ~prolific_pid), size = 5) +
  ggtitle('Cultural Similarity') +
  cowplot::theme_cowplot(font_size = 20) +
  theme(legend.position = 'none')

ggsave(here('pres/values.png'), width = 8, height = 6)

(mutate(survey, resp_education = factor(ifelse(resp_education == "Master's, doctorate, or other postgraduate degree", 'Advanced degree', as.character(resp_education)), levels = c('Less than high school', 'High school', "Some college", "Bachelor's degree", "Advanced degree"))) %>%
  cj(chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~ resp_education) %>%
  plot(group = 'resp_education', size = 5) +
  geom_vline(xintercept = .5, linewidth = .2) +
  theme(legend.position = 'right')) /
(plot(cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~ resp_politics),
        group = 'resp_politics', size = 5) +
  geom_vline(xintercept = .5, linewidth = .2) +
  theme(legend.position = 'right')) /
(plot(cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~resp_religion),
        group = 'resp_religion', size = 5) +
  geom_vline(xintercept = .5, linewidth = .2) +
  theme(legend.position = 'right')) &
  cowplot::theme_cowplot(font_size = 20) &
  xlim(c(.3, .7)) &
  labs(x = '')

ggsave(here('pres/mm1.png'), width = 8, height = 8)

(plot(cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~ resp_sexuality),
        group = 'resp_sexuality', size = 5) +
  geom_vline(xintercept = .5, linewidth = .2) +
  theme(legend.position = 'right')) /
(plot(cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~ resp_overpop),
        group = 'resp_overpop', size = 5) +
  geom_vline(xintercept = .5, linewidth = .2) +
  theme(legend.position = 'right')) /
(plot(cj(survey, chosen ~ sexuality, estimate = 'mm',
        weights = ~weight, id = ~prolific_pid, by = ~know_LG),
        group = 'know_LG', size = 5) +
  geom_vline(xintercept = .5, linewidth = .2) +
  theme(legend.position = 'right')) &
  cowplot::theme_cowplot(font_size = 20) &
  xlim(c(.3, .7)) &
  labs(x = '')

ggsave(here('pres/mm2.png'), width = 8, height = 8)
```





\newpage

# References

<div id="refs"></div>


