---
output:
  beamer_presentation:
    keep_tex: no
    incremental: no
    toc: no
    latex_engine: pdflatex
    slide_level: 2
    include:
      in_header: ucla_beamer.tex
    fig_width: 12.5

header-includes:
#   - \setbeameroption{show notes}   
                        
editor_options: 
  chunk_output_type: console


bibliography: "/Users/nathan/Documents/My Library.bib" 
# csl: apa.csl
link-citations: yes
linkcolor: gray


title: "How Sexuality Affects Evaluations of Immigrant Deservingness and Cultural Similarity: A Conjoint Survey Experiment"

author: |
  | Nathan I. Hoffmann, Department of Sociology, UCLA
  | Kristopher Velasco, Depatment of Sociology, Princeton
  
date: "PAA 2024 Annual Meeting"
# date: "`r format(Sys.time(), '%B %d, %Y')`"

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, cache = T, 
                      dpi = 300)
library(here)
library(huxtable)
library(haven)
library(patchwork)
library(cregg)
library(rdss)
library(DeclareDesign)
library(tidyverse)

options("yaml.eval.expr" = TRUE)

theme_set(theme_classic(base_family = 'Palatino') + 
            theme(legend.title=element_blank(),
                  panel.grid.major.y = element_line('grey80'),
                  legend.background = element_rect(fill = "transparent")))
ggplot <- function(...) ggplot2::ggplot(...) + scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2")
```

```{r load}
prolific <- read_csv(here('data', 'prolific.csv')) %>%
  filter(Status == 'APPROVED' | Status == 'AWAITING REVIEW')
col_names <- names(read_csv(here('data', 'survey.csv'), n_max = 0))
survey_raw <- read_csv(here('data', 'survey.csv'), col_names = col_names, skip = 3) %>%
  filter(PROLIFIC_PID %in% prolific$`Participant id`,
         PROLIFIC_PID != '644af405d31dd25adf037157', # failed attention check
         PROLIFIC_PID != '6048622d518a190008dfbe38', # extra person
         Finished == T)
# 
# not_approved <- prolific %>%
#   filter(Status != 'APPROVED') %>%
#   pull(`Participant id`)
# filter(survey_raw, PROLIFIC_PID %in% not_approved) %>%
#   select(Finished, PROLIFIC_PID)
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$prolific_pid)) %>%
#   arrange(`Participant id`) %>%
#   select(`Participant id`, Status)
# 
# unfinished_maybe <- survey_raw %>%
#   filter(Finished != T) %>%
#   pull(PROLIFIC_PID)
# finished_ids <- survey_raw %>%
#   filter(Finished == T) %>%
#   pull(PROLIFIC_PID)
# unfinished <- unfinished_maybe[!(unfinished_maybe %in% finished_ids)]
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   View()
# 
# survey_raw %>%
#   filter(Finished != T) %>%
#   View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished)
# 
# survey_raw %>%
#   filter(PROLIFIC_PID == '6111811553d54da81ce61f21') %>% View()
# 
# survey_raw %>%
#   filter(PROLIFIC_PID %in% unfinished) %>%
#   arrange(PROLIFIC_PID) %>%
#   select(PROLIFIC_PID, Finished)
#   group_by(PROLIFIC_PID) %>% count()
#   select(PROLIFIC_PID, everything()) %>% View()
# 
# survey_raw %>%
#   filter(!(PROLIFIC_PID %in% prolific$`Participant id`)) %>%
#   select(PROLIFIC_PID)
# 
# survey_raw %>%
#   arrange(PROLIFIC_PID) %>%
#   group_by(PROLIFIC_PID) %>%
#   filter(n()>1) %>% 
#   select(PROLIFIC_PID, everything()) %>%
#   View()
# 
# 
# prolific %>%
#   filter(!(`Participant id` %in% survey_raw$PROLIFIC_PID)) %>%
#   select(`Participant id`)
# 
# survey_raw %>% filter(PROLIFIC_PID %in% 
#                         c('5a91877e777df200015fa0f5',
#                           '608a58c50e40c85b2f5f94ec',
#                           '6111811553d54da81ce61f21',
#                           '60fd957e79d70d6be755ad8c')) %>% View()


# Attention check
  # survey_raw %>%
  #   filter(!str_detect(tolower(attention_color_5_TEXT), 'green') |
  #            !(str_detect(as.character(attention_number_6_TEXT), '9') |
  #               str_detect(tolower(as.character(attention_number_6_TEXT)), 'nine'))
  #          ) %>%
  #   mutate(minutes = `Duration (in seconds)`/60) %>%
  #   select(prolific_pid, attention_color_5_TEXT, attention_number_6_TEXT, minutes)



survey <- survey_raw %>%
  #mutate(choice1 = Q3, choice2 = Q3, choice3 = Q13, choice4 = Q13) %>%
  pivot_longer(c(gender1:reason4, rating1:value2, rating3:value4, 
                 rating5:value6, rating7:value8), 
               names_to = c('.value', 'number'), names_pattern = ('(.*)(\\d+)')) %>%
  filter(!is.na(gender)) %>%
  mutate(
    chosen = case_when(
      choice_a == 'Immigrant 1 should be admitted.' & number == 1 ~ 1,
      choice_a == 'Immigrant 2 should be admitted.' & number == 2 ~ 1,
      choice_b == 'Immigrant 3 should be admitted.' & number == 3 ~ 1,
      choice_b == 'Immigrant 4 should be admitted.' & number == 4 ~ 1,
      choice_c == 'Immigrant 5 should be admitted.' & number == 5 ~ 1,
      choice_c == 'Immigrant 6 should be admitted.' & number == 6 ~ 1,
      choice_d == 'Immigrant 7 should be admitted.' & number == 7 ~ 1,
      choice_d == 'Immigrant 8 should be admitted.' & number == 8 ~ 1,
      T ~ 0),
    value_chosen = case_when(
      value_a == 'Immigrant 1 has greater shared values with the U.S.' & number == 1 ~ 1,
      value_a == 'Immigrant 2 has greater shared values with the U.S.' & number == 2 ~ 1,
      value_b == 'Immigrant 3 has greater shared values with the U.S.' & number == 3 ~ 1,
      value_b == 'Immigrant 4 has greater shared values with the U.S.' & number == 4 ~ 1,
      value_c == 'Immigrant 5 has greater shared values with the U.S.' & number == 5 ~ 1,
      value_c == 'Immigrant 6 has greater shared values with the U.S.' & number == 6 ~ 1,
      value_d == 'Immigrant 7 has greater shared values with the U.S.' & number == 7 ~ 1,
      value_d == 'Immigrant 8 has greater shared values with the U.S.' & number == 8 ~ 1,
      T ~ 0),
    sexuality = factor(ifelse(sexuality %in% c('lesbian', 'gay'), 'lesbian or gay', 'straight'), 
                       levels = c('straight', 'lesbian or gay')),
    across(c(gender, sexuality, gdp, skill, lang, religion, reason), function(x) factor(x)),
    across(c(rating, value), function(x) as.numeric(substr(x, 1,1)))) %>%
  mutate(skill = recode(skill, 
                        'has a high school degree, and works as a restaurant manager' = 
                          'high school',
                        'has a primary school education, and works as a cleaner' = 
                          'primary school',
                        'has an MD, and works as a cardiologist' = 'MD'),
         reason = recode(reason, 'could not find work due to high unemployment' = 
                           'could not find work'),
         resp_religion_full = resp_religion,
         resp_religion = factor(case_when(
           resp_religion %in% c('Other Christian', '
                                Protestant (Baptist, Methodist, Non-denominational, Lutheran, Presbyterian, Pentecostal, Episcopalian, Reformed, Church of Christ, Jehovah’s Witness, etc.)',
                                'Roman Catholic (Catholic)') ~ 'Christian',
           resp_religion %in% c('Agnostic (not sure if there is a God)',
                                'Atheist (do not believe in God)',
                                'Nothing in particular') ~ 'Atheist/not religious',
           T ~ 'Other')),
         resp_politics = factor(ifelse(
             resp_politics %in% c('Independent', 'None of these'), 'other',
             resp_politics)),
         resp_sexuality = factor(case_when(
           resp_sexuality %in% c("I don't know the answer", 'Something else') ~ 'Other',
           resp_sexuality %in% c('Bisexual', 'Lesbian or gay') ~ 'Lesbian/gay/bisexual',
           resp_sexuality == 'Straight (that is, not gay or lesbian)' ~ 'Straight'
         )),
         resp_education = factor(resp_education),
         resp_pro_econ = resp_imm_support_1,
         resp_pro_job = resp_imm_support_2,
         resp_pro_tax = resp_imm_support_3,
         resp_pro_culture = resp_imm_support_4,
         resp_pro_help = resp_imm_support_5,
         resp_con_econ = resp_imm_support_6,
         resp_con_job = resp_imm_support_7,
         resp_con_welfare = resp_imm_support_8,
         resp_con_crime = resp_imm_support_9,
         resp_con_pop = resp_imm_support_10,
         resp_con_culture = resp_imm_support_11
  ) %>%
  mutate(BA = factor(case_when(
    resp_education %in% c("Bachelor's degree", "Master's, doctorate, or other postgraduate degree") ~ 'BA',
    !is.na(resp_education) ~ 'no BA')),
    resp_overpop = factor(case_when(
      resp_con_pop %in% c('Agree', 'Somewhat agree') ~ 'Agree',
      resp_con_pop %in% c('Disagree', 'Somewhat disagree') ~ 'Disgree')),
    know_LG = factor(case_when(resp_knowlg %in% c('No, none', "I'm not sure") ~ 'No', 
                        T ~ 'Yes'))
    )


# survey <- survey %>% slice(rep(row_number(), each = 10)) %>%
#   mutate(prolific_pid = 1:n())

```



# Introduction

- From 2008 to 2019, 140% increase in immigrants in same-sex couples (Hoffmann & Velasco 2023)
- Changing policy landscape in the U.S. and around the world
    + In 2011, President Obama moved to make queer refugees a "population of concern" 
    + End of Defense of Marriage Act (DOMA) allowed U.S. citizens and residents to sponsor visas of same-sex partners
    + Fleeing repression but also enabled by pro-LGBT policy
- Little known about how American citizens perceive these lesbian and gay (LG) migrants
- Competing theories of immigrant deservingness 
    + Cultural similarity, economic potential, humanitarian merit


# Research Questions

1. How do U.S. citizens evaluate sexuality when making determinations of immigrant deservingness for admission? How does sexuality compare more well studied topics like reason for migration and skill level of the immigrant? 

2. Are lesbian and gay immigrants perceived as more culturally similar to the U.S. compared to their heterosexual counterparts? And does this increase perceived deservingness? 

3. Do Americans' perceptions of sexual minority immigrants vary by their own political affiliation, religious identification, or sexuality?


<!-- # Hypotheses -->
<!-- - H1 (main effect): Lesbian/gay identity will have a positive effect, relative to straight identity.   -->
<!-- - H2 (mediation): Respondents who are more likely to choose lesbian/gay profiles for admission will choose them as having more shared values with the U.S., on average. Controlling for this measure of cultural similarity will attenuate the effect for lesbian/gay identity.   -->
<!-- - H3 (interaction): For lesbian/gay profiles, persecution will have a higher marginal mean than work as a reason for migration.   -->


<!-- Heterogeneous effects for marginal means for lesbian/gay identity:   -->
<!-- - H4a (education): Respondents with a bachelor's degree will have a higher marginal mean than other education levels -->
<!-- - H4b (political ideology): Democrats will have a higher marginal mean than Republicans   -->
<!-- - H4c (religion): Christians will have a lower marginal mean than other groups   -->
<!-- - H4d (sexuality): Lesbian/gay/bisexual respondents will have a higher marginal mean than straight respondents   -->
<!-- - H4e (opinion): Respondents who worry about immigration contributing to overpopulation will have higher marginal means    -->
<!-- - H4f (lesbian/gay contacts) Respondents who have lesbian/gay friends and family will have higher marginal means -->

<!-- - Cultural similarity: expect that Americans of different backgrounds will evaluate the cultural similarity of lesbian and gay migrants differently -->
<!-- - Economic potential: lesbians and gays often perceived to be wealthier than straights -->
<!-- - Humanitarian merit -->



# Data and Methods 
- Conjoint survey experiment of 1,650 U.S. citizen respondents using Prolific Academic, administered in summer 2023
- Respondents shown two vignettes varying four attributes: gender, country GDP, skill, language, religion, reason for migration, and sexuality
- Respondents choose one of the two hypothetical immigrants for admission and also which profile they see is more culturally similar
- Example profile: *"Immigrant 1 wishes to be admitted as an immigrant to the United States. She comes from a moderately wealthy country, has a primary school education, and works as a cleaner. She does not speak English, is Christian, and identifies as lesbian. She had to leave her country because she could not find work due to high unemployment."*  
- Average marginal component effects (AMCEs) and marginal means


# Key Findings
- LG profiles 2% more likely to be chosen for admission, but nonsignificant
- LG profiles 5% less likely to be seen as culturally similar  
    + But among profiles seen as culturally simialr, LG profiles more likelyto be chosen
- LG profiles fleeing persecution seen as slightly more deserving than straight ones fleeing persecution
- Democrats, atheists, sexual minorities, and respondents who know LG people are more likely to admit LG immigrants than straight ones.


## 
\begin{center} 
  \huge{\textcolor{uclablue}{Thank You!}}  
    \\
\end{center}

\begin{center} 
  Nathan I. Hoffmann (\textcolor{uclablue}{nathanihoff@ucla.edu}) \\
  Kristopher Velasco
\end{center}

\note{Thank you, and I look forward to your feedback}





